### 2024-08-25 Webpage Visualizations Code.Rmd
added r files

---
title: "Web Page Visualization Code"
author: "Emerson Johnston"
lastmodifeddate: "2024-08-24"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

# Maintenance and Cleaning
```{r Reset and Setup}
rm(list = ls()) 
knitr::opts_knit$set(root.dir = '/Users/emerson/Github/Usenet')
```

```{r Import necessary R libraries}
# Load all necessary libraries at once
library(tidyverse)
library(ggplot2)
library(dplyr)
library(igraph)
library(ggraph)
library(tidytext)
library(topicmodels)
```

```{r R Read and Clean CSVs}
# Load Directories
threads_directory <- "CSV Files/Threads"
comments_directory <- "CSV Files/Comments"

# Load the datasets
all_threads <- read.csv("CSV Files/Threads/combined_threads_cleaned.csv")
all_comments <- read.csv("CSV Files/Comments/combined_comments_cleaned.csv")

all_threads <- all_threads %>% drop_na()
all_comments <- all_comments %>% drop_na()

# Ensure the 'Date' columns are properly formatted as Date objects
all_comments$Date <- as.Date(all_comments$Date, format = "%Y-%m-%d")
all_threads$Date <- as.Date(all_threads$Date, format = "%Y-%m-%d")

# Filter the datasets to include only data before January 1, 1989
all_comments <- all_comments %>%
  filter(Date < as.Date("1989-01-01")) %>% filter(Date > as.Date("1982-01-01"))

all_threads <- all_threads %>%
  filter(Date < as.Date("1989-01-01")) %>% filter(Date > as.Date("1982-01-01"))

write.csv(all_threads, file.path(threads_directory, "threads_cleaned_82TO89.csv"), row.names = FALSE)
write.csv(all_comments, file.path(comments_directory, "comments_cleaned_82TO89.csv"), row.names = FALSE)
```

```{python Import necessary Python libraries}
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns
import numpy as np
import plotly.express as px
import plotly.graph_objects as go
import networkx as nx
import scipy
```

```{python Python Read CSVs}
all_comments = pd.read_csv("CSV Files/Comments/comments_cleaned_82TO89.csv")
all_threads = pd.read_csv("CSV Files/Threads/threads_cleaned_82TO89.csv")
```

# Initial Visualizations
```{python Distribution of Comments per Newsgroup}
plt.figure(figsize=(10, 6))
sns.countplot(data=all_comments, x='newsgroup', order=all_comments['newsgroup'].value_counts().index)
plt.title('Distribution of Comments per Newsgroup')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig('images and tables/distribution_of_comments_per_newsgroup.png')
plt.show()
```

```{python Number of Threads Over Time}
all_threads['Date'] = pd.to_datetime(all_threads['Date'])

plt.figure(figsize=(10, 6))
all_threads.groupby(all_threads['Date'].dt.to_period('M')).size().plot(kind='line')
plt.title('Number of Threads Over Time')
plt.xlabel('Month')
plt.ylabel('Number of Threads')
plt.tight_layout()
plt.savefig('images and tables/number_of_threads_over_time.png')
plt.show()
```

```{python Average Number of Comments per Thread by Newsgroup}
avg_comments_per_thread = all_threads.groupby('newsgroup')['Number.of.Messages'].mean().reset_index()

plt.figure(figsize=(10, 6))
sns.barplot(data=avg_comments_per_thread, x='newsgroup', y='Number.of.Messages', order=avg_comments_per_thread.sort_values('Number.of.Messages', ascending=False)['newsgroup'])
plt.title('Average Number of Comments per Thread by Newsgroup')
plt.xlabel('Newsgroup')
plt.ylabel('Average Number of Comments')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig('images and tables/average_comments_per_thread_by_newsgroup.png')
plt.show()
```

```{python Sentiment Score Distribution Across All Comments}
plt.figure(figsize=(10, 6))
sns.histplot(all_comments['SentimentScore'], bins=30, kde=True)
plt.title('Sentiment Score Distribution Across All Comments')
plt.xlabel('Sentiment Score')
plt.ylabel('Frequency')
plt.tight_layout()
plt.savefig('images and tables/sentiment_score_distribution_across_all_comments.png')
plt.show()
```

```{python Top 25 Most Active Users}
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns

# Get the top 25 authors by the number of comments
top_authors = all_comments['Author'].value_counts().head(25).index

# Filter the dataset to include only the top 25 authors
top_authors_data = all_comments[all_comments['Author'].isin(top_authors)]

# Calculate the number of comments by each of the top 25 authors in each newsgroup
comments_per_newsgroup = top_authors_data.groupby(['Author', 'newsgroup']).size().unstack(fill_value=0)

# Sort authors by total number of comments in descending order
comments_per_newsgroup['Total Comments'] = comments_per_newsgroup.sum(axis=1)
comments_per_newsgroup = comments_per_newsgroup.sort_values('Total Comments', ascending=True)

# Remove the 'Total Comments' column for plotting
comments_per_newsgroup = comments_per_newsgroup.drop(columns='Total Comments')

# Define a distinct color palette for newsgroups
distinct_colors = sns.color_palette('tab20', len(comments_per_newsgroup.columns))

# Plot a stacked bar plot without white lines between colors and with distinct colors
comments_per_newsgroup.plot(kind='barh', stacked=True, figsize=(12, 8), color=distinct_colors, edgecolor='none')

plt.title('Top 25 Most Active Users by Newsgroup')
plt.xlabel('Number of Comments')
plt.ylabel('Author')
plt.legend(title='Newsgroup', bbox_to_anchor=(1.05, 1), loc='upper left')
plt.tight_layout()

# Save the figure
plt.savefig('images and tables/top_25_most_active_users_by_newsgroup.png')
plt.show()
```

```{python Temporal Heatmap of Daily Activity by Newsgroup}
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns

# Convert 'Date.and.Time' to datetime and handle errors
all_comments['Date.and.Time'] = pd.to_datetime(all_comments['Date.and.Time'], errors='coerce')

# Check if there are any conversion issues and drop those rows
all_comments = all_comments.dropna(subset=['Date.and.Time'])

# Extract day of the week and hour
all_comments['DayOfWeek'] = all_comments['Date.and.Time'].dt.day_name()
all_comments['Hour'] = all_comments['Date.and.Time'].dt.hour

# Group data by DayOfWeek and Hour for all newsgroups combined
activity_data = all_comments.groupby(['DayOfWeek', 'Hour']).size().reset_index(name='Activity')

# Pivot table to prepare data for heatmap
heatmap_data = activity_data.pivot_table(index='Hour', columns='DayOfWeek', values='Activity', fill_value=0)

# Reorder days of the week for consistent display
day_order = ['Monday', 'Tuesday', 'Wednesday', 'Thursday', 'Friday', 'Saturday', 'Sunday']
heatmap_data = heatmap_data[day_order]

# Create the heatmap
plt.figure(figsize=(12, 8))
sns.heatmap(heatmap_data, cmap='viridis')
plt.title('Daily Activity Heatmap Across All Newsgroups')
plt.xlabel('Day of Week')
plt.ylabel('Hour of Day')
plt.tight_layout()
plt.savefig('images and tables/combined_daily_activity_heatmap.png')
plt.show()
```

```{python Word Clouds!}
import pandas as pd
from wordcloud import WordCloud
import matplotlib.pyplot as plt
from nltk.corpus import stopwords
import nltk

# Ensure NLTK stopwords are downloaded
nltk.download('stopwords')
stop_words = set(stopwords.words('english'))

# Combine all text data into one string for all comments
all_text = " ".join(all_comments['Full.Text'].dropna())

# Create word cloud for all comments
wordcloud_all = WordCloud(width=800, height=400, background_color='white', stopwords=stop_words, collocations=False).generate(all_text)

plt.figure(figsize=(10, 6))
plt.imshow(wordcloud_all, interpolation='bilinear')
plt.axis('off')
plt.title('Most Common Words in All Usenet Comments')
plt.tight_layout()
plt.savefig('images and tables/word_cloud_all_comments.png')
plt.show()

# Generate word clouds by newsgroup
for newsgroup in all_comments['newsgroup'].unique():
    # Filter comments for the current newsgroup
    group_text = " ".join(all_comments[all_comments['newsgroup'] == newsgroup]['Full.Text'].dropna())

    # Create word cloud for the specific newsgroup
    wordcloud_group = WordCloud(width=800, height=400, background_color='white', stopwords=stop_words, collocations=False).generate(group_text)

    plt.figure(figsize=(10, 6))
    plt.imshow(wordcloud_group, interpolation='bilinear')
    plt.axis('off')
    plt.title(f'Most Common Words in {newsgroup}')
    plt.tight_layout()
    plt.savefig(f'images and tables/word_cloud_{newsgroup}.png')
    plt.show()
```

```{python Growth of Newsgroups Over Time}
# Convert Date to datetime format
all_threads['Date'] = pd.to_datetime(all_threads['Date'])

# Calculate cumulative count of newsgroups created over time
plt.figure(figsize=(10, 6))
all_threads.groupby(all_threads['Date'].dt.to_period('M')).newsgroup.nunique().cumsum().plot(kind='line')
plt.title('Growth of Newsgroups Over Time')
plt.xlabel('Month')
plt.ylabel('Cumulative Number of Newsgroups')
plt.tight_layout()
plt.savefig('images and tables/growth_of_newsgroups_over_time.png')
plt.show()
```

```{python Author Engagement Scatter Plot}
# Calculate number of comments and threads per author
author_stats = all_comments.groupby('Author').agg({'Thread.ID': pd.Series.nunique, 'Unique_CommentID': 'count'}).reset_index()
author_stats.columns = ['Author', 'Threads_Initiated', 'Comments_Made']

plt.figure(figsize=(10, 6))
sns.scatterplot(data=author_stats, x='Threads_Initiated', y='Comments_Made', alpha=0.6)
plt.title('Author Engagement: Comments Made vs. Threads Initiated')
plt.xlabel('Number of Threads Initiated')
plt.ylabel('Number of Comments Made')
plt.tight_layout()
plt.savefig('images and tables/author_engagement_scatterplot.png')
plt.show()
```

# Sentiment Visualizations
```{python Average Sentiment Over Time Across All Newsgroups}
import pandas as pd
import matplotlib.pyplot as plt

# Ensure 'Date' is in datetime format
all_comments['Date'] = pd.to_datetime(all_comments['Date'])

# Group by month and calculate average sentiment
sentiment_over_time = all_comments.groupby(all_comments['Date'].dt.to_period('M'))['SentimentScore'].mean().reset_index()
sentiment_over_time['Date'] = sentiment_over_time['Date'].dt.to_timestamp()

plt.figure(figsize=(12, 6))
plt.plot(sentiment_over_time['Date'], sentiment_over_time['SentimentScore'], marker='o', linestyle='-')
plt.title('Average Sentiment Over Time Across All Newsgroups')
plt.xlabel('Date')
plt.ylabel('Average Sentiment Score')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig('images and tables/sentiment_over_time.png')
plt.show()
```

```{python Sentiment Distribution by Newsgroup Boxplot}
import seaborn as sns

plt.figure(figsize=(12, 6))
sns.boxplot(x='newsgroup', y='SentimentScore', data=all_comments)
plt.title('Sentiment Distribution by Newsgroup')
plt.xlabel('Newsgroup')
plt.ylabel('Sentiment Score')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig('images and tables/sentiment_distribution_by_newsgroup.png')
plt.show()
```

```{python Monthly Sentiment Heatmap by Newsgroup}
# Group by newsgroup and month to calculate average sentiment
monthly_sentiment = all_comments.groupby([all_comments['Date'].dt.to_period('M'), 'newsgroup'])['SentimentScore'].mean().reset_index()
monthly_sentiment['Date'] = monthly_sentiment['Date'].dt.to_timestamp()

# Pivot table for heatmap
heatmap_data = monthly_sentiment.pivot('newsgroup', 'Date', 'SentimentScore')

plt.figure(figsize=(12, 8))
sns.heatmap(heatmap_data, cmap='coolwarm', center=0)
plt.title('Monthly Sentiment Heatmap by Newsgroup')
plt.xlabel('Month')
plt.ylabel('Newsgroup')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig('images and tables/monthly_sentiment_heatmap.png')
plt.show()
```

```{python Sentiment Score Over Time by Newsgroup}
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns

# Ensure 'Date' is in datetime format
all_comments['Date'] = pd.to_datetime(all_comments['Date'])

# Group by month and newsgroup to calculate average sentiment
sentiment_by_newsgroup = all_comments.groupby([all_comments['Date'].dt.to_period('M'), 'newsgroup'])['SentimentScore'].mean().reset_index()
sentiment_by_newsgroup['Date'] = sentiment_by_newsgroup['Date'].dt.to_timestamp()

plt.figure(figsize=(14, 8))
sns.lineplot(data=sentiment_by_newsgroup, x='Date', y='SentimentScore', hue='newsgroup', marker='o')
plt.title('Average Sentiment Over Time by Newsgroup')
plt.xlabel('Date')
plt.ylabel('Average Sentiment Score')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig('images and tables/sentiment_over_time_by_newsgroup.png')
plt.show()
```

```{python Sentiment Polarity Distribution (Positive vs. Negative)}
# Define positive and negative sentiment based on threshold
positive_threshold = 0
all_comments['SentimentPolarity'] = all_comments['SentimentScore'].apply(lambda x: 'Positive' if x > positive_threshold else 'Negative')

plt.figure(figsize=(8, 6))
sns.countplot(data=all_comments, x='SentimentPolarity', palette=['red', 'green'])
plt.title('Sentiment Polarity Distribution')
plt.xlabel('Sentiment Polarity')
plt.ylabel('Number of Comments')
plt.tight_layout()
plt.savefig('images and tables/sentiment_polarity_distribution.png')
plt.show()
```

```{python Sentiment Trend Analysis with Rolling Average}
# Calculate rolling average of sentiment over time
all_comments['RollingSentiment'] = all_comments['SentimentScore'].rolling(window=30, min_periods=1).mean()

plt.figure(figsize=(12, 6))
plt.plot(all_comments['Date'], all_comments['RollingSentiment'], color='purple')
plt.title('Sentiment Trend Analysis with Rolling Average')
plt.xlabel('Date')
plt.ylabel('Rolling Average Sentiment Score (30-day window)')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig('images and tables/sentiment_trend_rolling_average.png')
plt.show()
```

```{python Top Words Associated with Positive and Negative Sentiments}
from wordcloud import WordCloud

# Separate positive and negative comments
positive_comments = " ".join(all_comments[all_comments['SentimentPolarity'] == 'Positive']['Full.Text'].dropna())
negative_comments = " ".join(all_comments[all_comments['SentimentPolarity'] == 'Negative']['Full.Text'].dropna())

# Create word cloud for positive sentiment
wordcloud_positive = WordCloud(width=800, height=400, background_color='white', stopwords=stop_words, collocations=False).generate(positive_comments)

plt.figure(figsize=(10, 6))
plt.imshow(wordcloud_positive, interpolation='bilinear')
plt.axis('off')
plt.title('Top Words in Positive Sentiment Comments')
plt.tight_layout()
plt.savefig('images and tables/word_cloud_positive_sentiment.png')
plt.show()

# Create word cloud for negative sentiment
wordcloud_negative = WordCloud(width=800, height=400, background_color='white', stopwords=stop_words, collocations=False).generate(negative_comments)

plt.figure(figsize=(10, 6))
plt.imshow(wordcloud_negative, interpolation='bilinear')
plt.axis('off')
plt.title('Top Words in Negative Sentiment Comments')
plt.tight_layout()
plt.savefig('images and tables/word_cloud_negative_sentiment.png')
plt.show()
```

# Network Visualizations
```{r Load R Libraries}
# Load necessary libraries
library(dplyr)
library(tidyr)
library(visNetwork)
library(igraph)  # Needed for community detection
library(RColorBrewer)  # For generating pastel colors
```

```{r Get Authors Metadata}
# Step 1: Calculate basic metadata for each author
metadata <- all_comments %>%
  group_by(Author) %>%
  summarize(
    total_threads = n_distinct(Thread.ID),  # Count distinct threads per author
    total_comments = n(),  # Total number of comments made by the author
    threads_started = sum(Thread_Relative_CommentID == "CM00001", na.rm = TRUE),  # Number of threads started by the author
    .groups = 'drop'
  )

# Step 2: Calculate comments per newsgroup for each author
comments_per_newsgroup <- all_comments %>%
  group_by(Author, newsgroup) %>%
  summarize(total_comments_in_newsgroup = n(), .groups = 'drop')

# Step 3: Pivot the newsgroup data to wide format to create separate columns for each newsgroup
comments_per_newsgroup_wide <- comments_per_newsgroup %>%
  pivot_wider(
    names_from = newsgroup,
    values_from = total_comments_in_newsgroup,
    values_fill = list(total_comments_in_newsgroup = 0)  # Fill missing values with 0
  )

# Step 4: Merge the metadata with the wide format newsgroup data
metadata <- metadata %>%
  left_join(comments_per_newsgroup_wide, by = "Author")

# Step 5: Calculate author influence based on the number of connections in the network
# Calculate the degree (number of connections) for each author in the graph
edges <- all_comments %>%
  filter(Thread.ID != "") %>%
  group_by(Thread.ID) %>%
  filter(n() > 1) %>%
  summarize(edgelist = list(combn(Author, 2, simplify = FALSE))) %>%
  unnest(edgelist) %>%
  unnest_wider(edgelist, names_sep = "") %>%
  rename(source = edgelist1, target = edgelist2) %>%
  filter(source != target) %>%
  group_by(source, target) %>%
  summarize(weight = n(), .groups = 'drop')

# Create graph object
graph <- igraph::graph_from_data_frame(edges, directed = FALSE)

# Calculate the degree for each author as their influence
author_influence <- data.frame(
  Author = igraph::V(graph)$name,
  influence = igraph::degree(graph)
)

# Step 6: Merge author influence into metadata
metadata <- metadata %>%
  left_join(author_influence, by = "Author")

# Step 7: Perform community detection using Louvain algorithm
communities <- cluster_louvain(graph)
membership <- membership(communities)

# Step 8: Create node_communities DataFrame
node_communities <- data.frame(
  name = V(graph)$name,  # Node names (authors)
  community = membership  # Community assignment
)

# Step 9: Sort the metadata DataFrame by total_comments in descending order
metadata <- metadata %>%
  arrange(desc(total_comments))

# Preview the updated metadata dataframe
print(metadata)
print(node_communities)  # Display node communities
```

```{r Create Edges and Nodes}
# Create top_authors list for the top 15 authors by influence
top_authors <- metadata %>%
  arrange(desc(influence)) %>%
  slice(1:20) %>%
  pull(Author)

# Filter metadata and comments data for only top authors
metadata <- metadata %>%
  filter(Author %in% top_authors)

comments_per_newsgroup_wide <- comments_per_newsgroup_wide %>%
  filter(Author %in% top_authors)

# Step 10: Create Edges and Nodes for the visualization

# Filter edges to include only those involving top authors
edges <- edges %>%
  filter(source %in% top_authors & target %in% top_authors)

# Prepare nodes data
nodes <- data.frame(
  name = top_authors,
  size = author_influence$influence[match(top_authors, author_influence$Author)],
  label = top_authors
)

# Merge nodes with their community data
nodes <- nodes %>%
  left_join(node_communities, by = "name")

# Add metadata and newsgroup comments in descending order to the title
nodes <- nodes %>%
  mutate(
    # Calculate the newsgroup comments section dynamically
    comments_per_newsgroup = sapply(name, function(author_name) {
      author_data <- comments_per_newsgroup_wide %>%
        filter(Author == author_name) %>%
        select(-Author) %>%
        pivot_longer(cols = everything(), names_to = "newsgroup", values_to = "comments") %>%
        arrange(desc(comments))

      paste(author_data$newsgroup, author_data$comments, sep = ": ", collapse = "<br>")
    }),

    # Prepare the title with the formatted metadata and comments per newsgroup
    title = paste0(
      "<div style='background-color: #f2f2f2; border: 2px solid #666666; padding: 5px;'>",  # Custom tooltip styling
      "<strong>", name, "</strong><br>",
      "Total Threads Participated: ", metadata$total_threads[match(name, metadata$Author)], "<br>",
      "Total Comments: ", metadata$total_comments[match(name, metadata$Author)], "<br>",
      "Threads Started: ", metadata$threads_started[match(name, metadata$Author)], "<br>",
      "Influence: ", metadata$influence[match(name, metadata$Author)], " (based on the number of connections)", "<br><br>",
      "<strong>Comments per Newsgroup</strong><br>",
      comments_per_newsgroup,
      "</div>"  # End of custom tooltip styling
    )
  )

# Identify current min and max sizes for nodes
current_min <- min(nodes$size, na.rm = TRUE)
current_max <- max(nodes$size, na.rm = TRUE)

# Define new desired range for node sizes
new_min <- 15  # Minimum size
new_max <- 30  # Maximum size

# Apply Min-Max scaling to the 'size' column
nodes <- nodes %>%
  mutate(
    size = ((size - current_min) / (current_max - current_min)) * (new_max - new_min) + new_min
  )

nodes
edges
summary(nodes)
summary(edges)
```

```{r Visualize the Graph}
# Libraries
library(dplyr)
library(tidyr)
library(visNetwork)
library(igraph)  # Needed for community detection
library(RColorBrewer)  # For generating pastel colors

# Convert node names to zero-based indices
nodes <- nodes %>%
  mutate(id = 0:(n() - 1))  # Create a new 'id' column for nodes

# Convert 'source' and 'target' in edges to indices using the 'name' to 'id' mapping
edges <- edges %>%
  mutate(
    from = match(source, nodes$name) - 1,  # Zero-based index
    to = match(target, nodes$name) - 1     # Zero-based index
  )

# Automatically assign colors to communities using RColorBrewer
num_communities <- length(unique(node_communities$community))
colors <- brewer.pal(min(num_communities, 9), "Set1")  # Use Set1 palette for distinct colors

# If you have more than 9 communities and need more colors, you can create a larger palette
# by repeating or expanding the Set1 palette
if (num_communities > 9) {
  colors <- colorRampPalette(brewer.pal(9, "Set1"))(num_communities)
}
# Merge nodes with their community data and assign colors automatically
nodes <- nodes %>%
  mutate(color = colors[community])

# Create a network visualization with a force-directed layout
network_graph <- visNetwork(nodes, edges, width = "100vw", height = "100vh") %>%
  visNodes(
    size = nodes$size * 5,
    font = list(size = 15),
    color = list(
      border = "black",
      highlight = "red"
    ),
    title = nodes$title  # Use the title for hover popups
  ) %>%
  visEdges(
    width = ~weight,
    color = list(color = 'gray', highlight = 'red'),
    smooth = list(enabled = TRUE, type = "dynamic", roundness = 0.5)  # Enable smooth dynamic edges with medium roundness
  ) %>%
  visOptions(
    highlightNearest = list(enabled = TRUE, hover = TRUE),
    nodesIdSelection = list(enabled = TRUE)
  ) %>%
  visPhysics(
    stabilization = TRUE,
    solver = "barnesHut",
    barnesHut = list(gravitationalConstant = -8000, springLength = 100, springConstant = 0.01)
  ) %>%
  visInteraction(
    dragNodes = TRUE,
    dragView = TRUE,
    zoomView = TRUE
  ) %>%
  visLayout(
    improvedLayout = TRUE
  )

# Display the network graph in the RStudio Viewer
network_graph

# Save the network graph to an HTML file with full width and height
visSave(network_graph, file = "Images and Tables/network_graph.html")

# Step 4: Add the custom legend directly into the HTML file after it is saved
html_legend <- '
<div style="position: absolute; bottom: 20px; right: 20px; background-color: white; border: 1px solid #666; padding: 10px; border-radius: 5px; font-family: Arial, sans-serif;">
  <div style="margin-bottom: 5px;"><strong>Color</strong> = Community (Louvain)</div>
  <div><strong>Node Size</strong> = Influence</div>
</div>
'

# Inject the legend into the HTML file
html_file <- "Images and Tables/network_graph.html"
html_content <- readLines(html_file)
html_content <- c(html_content, html_legend)
writeLines(html_content, html_file)
```

### 2024-08-25 Webpage Visualizations Code.Rmd
changed files

@@
 all_threads.groupby(all_threads['Date'].dt.to_period('M')).size().plot(kind='line')
-plt.title('Number of Threads Over Time')
+plt.title('Number of Threads Across All Newsgroups Over Time')
 plt.xlabel('Month')

### 2024-08-25 Scripts - Data Cleaning and Visualizations/CSV Cleaning.Rmd
changed some structure

---
title: "Usenet Project - CSV Cleaning"
author: "Emerson Johnston"
lastmodifeddate: "2024-08-07"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

# Old Read and Merge (DONT RUN)
netmed_threads <- read.csv("CSV Files/Threads/netmed_threads.csv")
netmotss_threads <- read.csv("CSV Files/Threads/netmotss_threads.csv")
netnews_threads <- read.csv("CSV Files/Threads/netnews_threads.csv")
netpolitics_threads <- read.csv("CSV Files/Threads/netpolitics_threads.csv")
netreligion_threads <- read.csv("CSV Files/Threads/netreligion_threads.csv")
netsingles_threads <- read.csv("CSV Files/Threads/netsingles_threads.csv")

netmed_comments <- read.csv("CSV Files/Comments/netmed_comments.csv")
netmotss_comments <- read.csv("CSV Files/Comments/netmotss_comments.csv")
netnews_comments <- read.csv("CSV Files/Comments/netnews_comments.csv")
netpolitics_comments <- read.csv("CSV Files/Comments/netpolitics_comments.csv")
netreligion_comments <- read.csv("CSV Files/Comments/netreligion_comments.csv")
netsingles_comments <- read.csv("CSV Files/Comments/netsingles_comments.csv")

netmed_threads$newsgroup <- "netmed"
netmotss_threads$newsgroup <- "netmotss"
netnews_threads$newsgroup <- "netnews"
netpolitics_threads$newsgroup <- "netpolitics"
netreligion_threads$newsgroup <- "netreligion"
netsingles_threads$newsgroup <- "netsingles"

all_threads <- rbind(netmed_threads, netmotss_threads, netnews_threads, netpolitics_threads, netreligion_threads, netsingles_threads)

netmed_comments$newsgroup <- "netmed"
netmotss_comments$newsgroup <- "netmotss"
netnews_comments$newsgroup <- "netnews"
netpolitics_comments$newsgroup <- "netpolitics"
netreligion_comments$newsgroup <- "netreligion"
netsingles_comments$newsgroup <- "netsingles"

all_comments <- rbind(netmed_comments, netmotss_comments, netnews_comments, netpolitics_comments, netreligion_comments, netsingles_comments)

threads_directory <- "CSV Files/Threads"
comments_directory <- "CSV Files/Comments"

write.csv(all_threads, file.path(threads_directory, "combined_threads.csv"), row.names = FALSE)
write.csv(all_comments, file.path(comments_directory, "combined_comments.csv"), row.names = FALSE)
---

---

# Maintainence

## Reset
```{r}
rm(list = ls()) 
setwd("/Users/emerson/Github/Usenet")
```

## Loading Libraries
```{r}
library(tidyverse)
library(readr)
library(webshot)
library(htmltools)
```
## Read and Clean CSVs
```{r}
# Load necessary libraries
library(dplyr)

# Load Directories
threads_directory <- "CSV Files/Threads"
comments_directory <- "CSV Files/Comments"

# Load the datasets
all_threads <- read.csv("CSV Files/Threads/combined_threads.csv")
all_comments <- read.csv("CSV Files/Comments/combined_comments.csv")

# Assign unique identifiers to newsgroups
newsgroup_ids <- c("netmed" = "NG01", "netmotss" = "NG02", "netnews" = "NG03",
                   "netpolitics" = "NG04", "netreligion" = "NG05", "netsingles" = "NG06")

# Update the all_threads dataset
all_threads <- all_threads %>%
  # Map newsgroup names to IDs and keep the original newsgroup column
  mutate(newsgroup_ID = factor(newsgroup, levels = names(newsgroup_ids), labels = newsgroup_ids),
         # Generate Unique Thread ID
         Unique_ThreadID = paste(newsgroup_ID, ThreadID, sep = "_")) %>%
  # Reorder columns: Unique_ThreadID, newsgroup, newsgroup_ID, followed by the rest
  select(Unique_ThreadID, newsgroup, newsgroup_ID, everything()) %>%
  # Rename ThreadID to NG_Relative_ThreadID
  rename(NG_Relative_ThreadID = ThreadID)

# Update the all_comments dataset
all_comments <- all_comments %>%
  # Map newsgroup names to IDs and keep the original newsgroup column
  mutate(newsgroup_ID = factor(newsgroup, levels = names(newsgroup_ids), labels = newsgroup_ids),
         # Generate Unique Comment ID
         Unique_CommentID = paste(newsgroup_ID, Unique.Comment.ID, sep = "_"),
         # Retain old Unique.Comment.ID as NG_Relative_CommentID
         NG_Relative_CommentID = Unique.Comment.ID,
         # Retain old Thread.ID as NG_Relative_ThreadID
         NG_Relative_ThreadID = Thread.ID, 
         # Generate new newsgroup.thread.id
         Thread.ID = paste(newsgroup_ID, Thread.ID, sep = "_"),
         # Retain old Comment.ID as Thread_Relative_CommentID
         Thread_Relative_CommentID = Comment.ID) %>%
  # Reorder columns: Unique_CommentID, newsgroup, newsgroup_ID, followed by the rest
  select(Unique_CommentID, newsgroup, newsgroup_ID, Thread.ID, NG_Relative_CommentID, NG_Relative_ThreadID, Thread_Relative_CommentID, everything()) %>%
  # Drop the old Unique.Comment.ID and Comment.ID columns
  select(-Unique.Comment.ID, -Comment.ID)

# Display the updated dataframes (optional)
head(all_threads)
head(all_comments)
```
## Fix Date and Time Columns
```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)

# Function to clean the datetime strings
clean_datetime <- function(dt_str) {
  gsub("[^[:alnum:] [:punct:]]", "", dt_str)
}

# Clean the Date.and.Time column
all_comments$Date.and.Time <- sapply(all_comments$Date.and.Time, clean_datetime)

# Convert the cleaned Date.and.Time to POSIXct
all_comments$Date.and.Time <- as.POSIXct(all_comments$Date.and.Time, format = "%b %d, %Y, %I:%M:%S%p")

all_comments$Hour <- as.numeric(format(all_comments$Date.and.Time, "%H"))
all_comments$Date <- as.Date(all_comments$Date.and.Time)

all_threads$Date <- as.Date(all_threads$Date, format = "%m/%d/%y")
```

## Run and Sentiment Scores
```{r} 
library(syuzhet)
all_comments <- all_comments %>% mutate(SentimentScore = get_sentiment(Full.Text, method = "afinn"))
```

## Save Cleaned CSVs to File
```{r}
write.csv(all_threads, file.path(threads_directory, "combined_threads_cleaned.csv"), row.names = FALSE)
write.csv(all_comments, file.path(comments_directory, "combined_comments_cleaned.csv"), row.names = FALSE)
```

# Descriptive Statistics

## Primary
```{r}
# Load necessary library
library(dplyr)
library(sjPlot)

# Calculate statistics using dplyr
summary_df <- all_comments %>%
  group_by(newsgroup) %>%
  summarize(
    Threads = n_distinct(Thread.ID),
    Comments = n(),
    Authors = n_distinct(Author),
    Avg_Comments_Per_Thread = Comments / Threads,
    Avg_Sentiment_Score = mean(SentimentScore, na.rm = TRUE)
  )

# Add a totals row
totals <- summary_df %>%
  summarize(
    newsgroup = "Total",
    Threads = sum(Threads),
    Comments = sum(Comments),
    Authors = n_distinct(all_comments$Author),
    Avg_Comments_Per_Thread = sum(Comments) / sum(Threads),
    Avg_Sentiment_Score = mean(all_comments$SentimentScore, na.rm = TRUE)
  )

# Combine the summary with the totals row
summary_df <- bind_rows(summary_df, totals)

# Print the summary data frame with totals
tab_df(summary_df, file = "Images and Tables/descriptive_statistics_table.html")
```

```{r}
library(knitr)
library(kableExtra)

# Create the table
summary_table <- kable(summary_df, format = "html", table.attr = "style='width:100%;'") %>%
  kable_styling(full_width = FALSE) %>%
  row_spec(0, bold = TRUE) %>%  # Make the first row bold
  row_spec(nrow(summary_df), hline_after = TRUE)  # Add a line after the second to last row

# Print the table
summary_table
```

## Keyword Search Statistics
```{r}
# Load necessary library
library(dplyr)

# List of extended keywords and phrases
keywords <- c("aids", "hiv", "acquired immune deficiency syndrome", "human immunodeficiency virus",
              "gay plague", "gay cancer", "kaposi's sarcoma", "pneumocystis pneumonia",
              "homosexual disease", "gay disease", "gay fear", "fear of gay", "fear of homosexual",
              "sexual orientation disease")

# Function to flag comments with keywords
flag_keywords <- function(text) {
  # Convert text to lowercase
  text <- tolower(text)
  # Check if any keyword is present
  grepl(paste(keywords, collapse = "|"), text)
}

# Add a column to indicate if the comment contains any keyword
all_comments <- all_comments %>%
  mutate(Contains_Keyword = flag_keywords(Full.Text))

# Identify threads with at least one comment containing a keyword
threads_with_keywords <- all_comments %>%
  filter(Contains_Keyword) %>%
  distinct(Thread.ID) %>%
  pull(Thread.ID)

# Filter comments in threads with at least one keyword
comments_in_keyword_threads <- all_comments %>%
  filter(Thread.ID %in% threads_with_keywords)

# Group by newsgroup and calculate required statistics
keywords_summary_df <- comments_in_keyword_threads %>%
  group_by(newsgroup) %>%
  summarize(
    Comments_with_Keywords = sum(Contains_Keyword),
    Conversations_Mentioned_In = n_distinct(Thread.ID),
    Total_Comments_In_Threads = n(),
    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100
  )

# Add a totals row
totals <- keywords_summary_df %>%
  summarize(
    newsgroup = "Total",
    Comments_with_Keywords = sum(Comments_with_Keywords),
    Conversations_Mentioned_In = sum(Conversations_Mentioned_In),
    Total_Comments_In_Threads = sum(Total_Comments_In_Threads),
    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100
  )

# Combine the summary with the totals row
keywords_summary_df <- bind_rows(keywords_summary_df, totals)

# Print the keyword summary data frame with totals
print(keywords_summary_df)
```

## Save Keyword CSVs to File
```{r}
# Collect all related threads and comments
related_threads <- all_threads %>%
  filter(Unique_ThreadID %in% threads_with_keywords) %>%
  filter(Date <= as.Date("1988-12-31"))

related_comments <- all_comments %>%
  filter(Thread.ID %in% threads_with_keywords) %>%
  filter(Date <= as.Date("1988-12-31"))

# Write the related threads and comments to CSV files
write.csv(related_threads, file.path(threads_directory, "aids_related_threads.csv"), row.names = FALSE)
write.csv(related_comments, file.path(comments_directory, "aids_related_comments.csv"), row.names = FALSE)
```

### 2024-08-25 Scripts - Archive Scraping/comment_scraper.py

@@ -1,0 +1,84 @@
+import pandas as pd
+import requests
+from bs4 import BeautifulSoup
+import os
+
+# Function to extract comments from a given link
+def extract_comments(url, thread_id):
+    comments_data = []
+    response = requests.get(url)
+    soup = BeautifulSoup(response.content, 'html.parser')
+
+    comments = soup.find_all('section', class_='BkrUxb')  # Find all comment sections
+
+    for i, comment in enumerate(comments):
+        comment_id = f"CM{i + 1:05}"
+        unique_comment_id = f"{thread_id}_{comment_id}"
+
+        # Extracting author name
+        author_tag = comment.find('h3', class_='s1f8Zd')
+        author_name = author_tag.get_text() if author_tag else "Unknown"
+
+        # Extracting date and time
+        date_tag = comment.find('span', class_='zX2W9c')
+        date_time = date_tag.get_text() if date_tag else "Unknown"
+
+        # Extracting full text
+        text_tag = comment.find('div', class_='ptW7te')
+        full_text = text_tag.get_text(separator='\n').strip() if text_tag else "No text"
+
+        # Extracting data-doc-id (url-string)
+        data_doc_id = comment.get('data-doc-id', 'Unknown')
+
+        # Storing the extracted data
+        comment_data = {
+            'Thread ID': thread_id,
+            'Comment ID': comment_id,
+            'Unique Comment ID': unique_comment_id,
+            'Author': author_name,
+            'Date and Time': date_time,
+            'Full Text': full_text,
+            'URL String': data_doc_id
+        }
+        comments_data.append(comment_data)
+
+    return comments_data
+
+# Main function to process the CSV file
+def process_csv(input_csv_path):
+    # Load the CSV file
+    data = pd.read_csv(input_csv_path)
+
+    # Check if the required columns exist
+    required_columns = ['ThreadID', 'URL']
+    for col in required_columns:
+        if col not in data.columns:
+            print(f"Error: Column '{col}' not found in the CSV file. Available columns: {data.columns}")
+            return
+
+    # Determine the output CSV file name
+    base_name = os.path.basename(input_csv_path)
+    output_base_name = base_name.replace('_threads', '_comments')
+    output_directory = '/Users/emerson/Github/usenet_early_histories_project/CSV Files/Comments/'
+    output_csv_path = os.path.join(output_directory, output_base_name)
+
+    # Iterate over each URL and collect comments
[…]

### 2024-08-25 Scripts - Archive Scraping/thread_scraper.py

@@ -1,0 +1,123 @@
+import csv
+import os  # Ensure the os module is imported as it should be
+from selenium import webdriver
+from selenium.webdriver.chrome.service import Service
+from selenium.webdriver.chrome.options import Options
+from selenium.webdriver.common.by import By
+from selenium.webdriver.support.ui import WebDriverWait
+from selenium.webdriver.support import expected_conditions as EC
+from webdriver_manager.chrome import ChromeDriverManager
+from bs4 import BeautifulSoup
+import time
+
+def main():
+    # Setup Chrome options
+    options = Options()
+    options.add_argument('--no-sandbox')
+    options.add_argument('--disable-dev-shm-usage')
+
+    # Setup the Chrome service
+    service = Service(ChromeDriverManager().install())
+    driver = webdriver.Chrome(service=service, options=options)
+
+    # Open the target webpage
+    newsgroup_url = "https://groups.google.com/g/net.news"
+    driver.get(newsgroup_url)
+
+    # Extract newsgroup name and format it for filename
+    newsgroup = newsgroup_url.split("/g/")[1].replace('.', '')
+    csv_filename = f"{newsgroup}_threads.csv"
+
+    # Ensure the output directory exists
+    output_directory = '/Users/emerson/Github/usenet_early_histories_project/CSV Files/Threads'
+    os.makedirs(output_directory, exist_ok=True)
+
+    # Determine the full output file path
+    output_filepath = os.path.join(output_directory, csv_filename)
+
+    # Initialize list to store all thread data
+    all_threads = []
+    total_threads = 0  # To store the total number of threads
+
+    try:
+        # Extract the total number of threads from the page
+        time.sleep(5)  # Ensure the page loads
+        soup = BeautifulSoup(driver.page_source, 'html.parser')
+        total_threads_element = soup.find("div", class_="aEb7Ed")
+        if total_threads_element:
+            total_threads_text = total_threads_element.text.split()[-1]
+            total_threads = int(total_threads_text.replace(",", ""))  # Remove commas and convert to int
+            print(f"Total threads: {total_threads}")
+
+        # Set starting counter for IDs
+        thread_id_counter = total_threads
+
+        while thread_id_counter > 0:
+            # Extract the page's HTML and parse it
+            soup = BeautifulSoup(driver.page_source, 'html.parser')
+
+            # Find all thread entries on the page
+            threads = soup.find_all("div", role="row")
+            for thread in threads:
+                try:
[…]

### 2024-08-25 Scripts - Data Cleaning and Visuals/_Webpage Visualizations Code.Rmd
cleaning up file tree even more
fixed r connection

--- 2024-08-25 Webpage Visualizations Code.Rmd
@@
 rm(list = ls()) 
-knitr::opts_knit$set(root.dir = '/Users/emerson/Github/Usenet')
+knitr::opts_knit$set(root.dir = '/Users/emerson/Github/usenet_early_histories_project')
 ```
@@
 # Load Directories
-threads_directory <- "CSV Files/Threads"
-comments_directory <- "CSV Files/Comments"
+threads_directory <- "/Users/emerson/Github/usenet_early_histories_project/CSV Files/Threads"
+comments_directory <- "/Users/emerson/Github/usenet_early_histories_project/CSV Files/Comments"
 
 # Load the datasets
-all_threads <- read.csv("CSV Files/Threads/combined_threads_cleaned.csv")
-all_comments <- read.csv("CSV Files/Comments/combined_comments_cleaned.csv")
+all_threads <- read.csv("/Users/emerson/Github/usenet_early_histories_project/CSV Files/Threads/combined_threads_cleaned.csv")
+all_comments <- read.csv("/Users/emerson/Github/usenet_early_histories_project/CSV Files/Comments/combined_comments_cleaned.csv")
 
@@
 ```{python Python Read CSVs}
-all_comments = pd.read_csv("CSV Files/Comments/comments_cleaned_82TO89.csv")
-all_threads = pd.read_csv("CSV Files/Threads/threads_cleaned_82TO89.csv")
+all_comments = pd.read_csv("/Users/emerson/Github/usenet_early_histories_project/CSV Files/Comments/comments_cleaned_82TO89.csv")
+all_threads = pd.read_csv("/Users/emerson/Github/usenet_early_histories_project/CSV Files/Threads/threads_cleaned_82TO89.csv")
 ```
@@
 plt.tight_layout()
-plt.savefig('images and tables/distribution_of_comments_per_newsgroup.png')
+plt.savefig('/Users/emerson/Github/usenet_early_histories_project/images and tables/distribution_of_comments_per_newsgroup.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/number_of_threads_over_time.png')
+plt.savefig('/Users/emerson/Github/usenet_early_histories_project/images and tables/number_of_threads_over_time.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/average_comments_per_thread_by_newsgroup.png')
+plt.savefig('/Users/emerson/Github/usenet_early_histories_project/images and tables/average_comments_per_thread_by_newsgroup.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/sentiment_score_distribution_across_all_comments.png')
+plt.savefig('/Users/emerson/Github/usenet_early_histories_project/images and tables/sentiment_score_distribution_across_all_comments.png')
 plt.show()
@@
 # Save the figure
-plt.savefig('images and tables/top_25_most_active_users_by_newsgroup.png')
+plt.savefig('/Users/emerson/Github/usenet_early_histories_project/images and tables/top_25_most_active_users_by_newsgroup.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/combined_daily_activity_heatmap.png')
+plt.savefig('/Users/emerson/Github/usenet_early_histories_project/images and tables/combined_daily_activity_heatmap.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/word_cloud_all_comments.png')
+plt.savefig('/Users/emerson/Github/usenet_early_histories_project/images and tables/word_cloud_all_comments.png')
 plt.show()
@@
     plt.tight_layout()
-    plt.savefig(f'images and tables/word_cloud_{newsgroup}.png')
+    plt.savefig(f'/Users/emerson/Github/usenet_early_histories_project/images and tables/word_cloud_{newsgroup}.png')
     plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/growth_of_newsgroups_over_time.png')
+plt.savefig('/Users/emerson/Github/usenet_early_histories_project/images and tables/growth_of_newsgroups_over_time.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/author_engagement_scatterplot.png')
+plt.savefig('/Users/emerson/Github/usenet_early_histories_project/images and tables/author_engagement_scatterplot.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/sentiment_over_time.png')
+plt.savefig('/Users/emerson/Github/usenet_early_histories_project/images and tables/sentiment_over_time.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/sentiment_distribution_by_newsgroup.png')
+plt.savefig('/Users/emerson/Github/usenet_early_histories_project/images and tables/sentiment_distribution_by_newsgroup.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/monthly_sentiment_heatmap.png')
+plt.savefig('/Users/emerson/Github/usenet_early_histories_project/images and tables/monthly_sentiment_heatmap.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/sentiment_over_time_by_newsgroup.png')
+plt.savefig('/Users/emerson/Github/usenet_early_histories_project/images and tables/sentiment_over_time_by_newsgroup.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/sentiment_polarity_distribution.png')
+plt.savefig('/Users/emerson/Github/usenet_early_histories_project/images and tables/sentiment_polarity_distribution.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/sentiment_trend_rolling_average.png')
+plt.savefig('/Users/emerson/Github/usenet_early_histories_project/images and tables/sentiment_trend_rolling_average.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/word_cloud_positive_sentiment.png')
+plt.savefig('/Users/emerson/Github/usenet_early_histories_project/images and tables/word_cloud_positive_sentiment.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/word_cloud_negative_sentiment.png')
+plt.savefig('/Users/emerson/Github/usenet_early_histories_project/images and tables/word_cloud_negative_sentiment.png')
 plt.show()
@@
 # Save the network graph to an HTML file with full width and height
-visSave(network_graph, file = "Images and Tables/network_graph.html")
+visSave(network_graph, file = "/Users/emerson/Github/usenet_early_histories_project/images and tables/network_graph.html")
 
@@
 # Inject the legend into the HTML file
-html_file <- "Images and Tables/network_graph.html"
+html_file <- "/Users/emerson/Github/usenet_early_histories_project/images and tables/network_graph.html"
 html_content <- readLines(html_file)

### 2024-08-25 Scripts - Data Cleaning and Visuals/_Webpage Visualizations Code.Rmd
changed directory locations and such

--- 2024-08-25 Webpage Visualizations Code.Rmd
@@
 rm(list = ls()) 
-knitr::opts_knit$set(root.dir = '/Users/emerson/Github/Usenet')
+knitr::opts_knit$set(root.dir = '/Users/emerson/Github/usenet_AIDs_discourses_webpage')
 ```
@@
 # Load Directories
-threads_directory <- "CSV Files/Threads"
-comments_directory <- "CSV Files/Comments"
+threads_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads"
+comments_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments"
 
 # Load the datasets
-all_threads <- read.csv("CSV Files/Threads/combined_threads_cleaned.csv")
-all_comments <- read.csv("CSV Files/Comments/combined_comments_cleaned.csv")
+all_threads <- read.csv("/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads/combined_threads_cleaned.csv")
+all_comments <- read.csv("/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments/combined_comments_cleaned.csv")
 
@@
 ```{python Python Read CSVs}
-all_comments = pd.read_csv("CSV Files/Comments/comments_cleaned_82TO89.csv")
-all_threads = pd.read_csv("CSV Files/Threads/threads_cleaned_82TO89.csv")
+all_comments = pd.read_csv("/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments/comments_cleaned_82TO89.csv")
+all_threads = pd.read_csv("/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads/threads_cleaned_82TO89.csv")
 ```
@@
 plt.tight_layout()
-plt.savefig('images and tables/distribution_of_comments_per_newsgroup.png')
+plt.savefig('/Users/emerson/Github/usenet_AIDs_discourses_webpage/images and tables/distribution_of_comments_per_newsgroup.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/number_of_threads_over_time.png')
+plt.savefig('/Users/emerson/Github/usenet_AIDs_discourses_webpage/images and tables/number_of_threads_over_time.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/average_comments_per_thread_by_newsgroup.png')
+plt.savefig('/Users/emerson/Github/usenet_AIDs_discourses_webpage/images and tables/average_comments_per_thread_by_newsgroup.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/sentiment_score_distribution_across_all_comments.png')
+plt.savefig('/Users/emerson/Github/usenet_AIDs_discourses_webpage/images and tables/sentiment_score_distribution_across_all_comments.png')
 plt.show()
@@
 # Save the figure
-plt.savefig('images and tables/top_25_most_active_users_by_newsgroup.png')
+plt.savefig('/Users/emerson/Github/usenet_AIDs_discourses_webpage/images and tables/top_25_most_active_users_by_newsgroup.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/combined_daily_activity_heatmap.png')
+plt.savefig('/Users/emerson/Github/usenet_AIDs_discourses_webpage/images and tables/combined_daily_activity_heatmap.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/word_cloud_all_comments.png')
+plt.savefig('/Users/emerson/Github/usenet_AIDs_discourses_webpage/images and tables/word_cloud_all_comments.png')
 plt.show()
@@
     plt.tight_layout()
-    plt.savefig(f'images and tables/word_cloud_{newsgroup}.png')
+    plt.savefig(f'/Users/emerson/Github/usenet_AIDs_discourses_webpage/images and tables/word_cloud_{newsgroup}.png')
     plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/growth_of_newsgroups_over_time.png')
+plt.savefig('/Users/emerson/Github/usenet_AIDs_discourses_webpage/images and tables/growth_of_newsgroups_over_time.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/author_engagement_scatterplot.png')
+plt.savefig('/Users/emerson/Github/usenet_AIDs_discourses_webpage/images and tables/author_engagement_scatterplot.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/sentiment_over_time.png')
+plt.savefig('/Users/emerson/Github/usenet_AIDs_discourses_webpage/images and tables/sentiment_over_time.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/sentiment_distribution_by_newsgroup.png')
+plt.savefig('/Users/emerson/Github/usenet_AIDs_discourses_webpage/images and tables/sentiment_distribution_by_newsgroup.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/monthly_sentiment_heatmap.png')
+plt.savefig('/Users/emerson/Github/usenet_AIDs_discourses_webpage/images and tables/monthly_sentiment_heatmap.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/sentiment_over_time_by_newsgroup.png')
+plt.savefig('/Users/emerson/Github/usenet_AIDs_discourses_webpage/images and tables/sentiment_over_time_by_newsgroup.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/sentiment_polarity_distribution.png')
+plt.savefig('/Users/emerson/Github/usenet_AIDs_discourses_webpage/images and tables/sentiment_polarity_distribution.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/sentiment_trend_rolling_average.png')
+plt.savefig('/Users/emerson/Github/usenet_AIDs_discourses_webpage/images and tables/sentiment_trend_rolling_average.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/word_cloud_positive_sentiment.png')
+plt.savefig('/Users/emerson/Github/usenet_AIDs_discourses_webpage/images and tables/word_cloud_positive_sentiment.png')
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/word_cloud_negative_sentiment.png')
+plt.savefig('/Users/emerson/Github/usenet_AIDs_discourses_webpage/images and tables/word_cloud_negative_sentiment.png')
 plt.show()
@@
 # Save the network graph to an HTML file with full width and height
-visSave(network_graph, file = "Images and Tables/network_graph.html")
+visSave(network_graph, file = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/images and tables/network_graph.html")
 
@@
 # Inject the legend into the HTML file
-html_file <- "Images and Tables/network_graph.html"
+html_file <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/images and tables/network_graph.html"
 html_content <- readLines(html_file)

### 2024-08-25 Scripts - Archive Scraping/comment_scraper.py

@@ -59,7 +59,7 @@ def process_csv(input_csv_path):
     # Determine the output CSV file name
     base_name = os.path.basename(input_csv_path)
     output_base_name = base_name.replace('_threads', '_comments')
-    output_directory = '/Users/emerson/Github/usenet_early_histories_project/CSV Files/Comments/'
+    output_directory = '/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments/'
     output_csv_path = os.path.join(output_directory, output_base_name)
 
     # Iterate over each URL and collect comments
@@ -80,5 +80,5 @@ def process_csv(input_csv_path):
     print(f"Comments successfully saved to {output_csv_path}")
 
 # Example usage with the provided file path
-input_csv_path = '/Users/emerson/Github/usenet_early_histories_project/CSV Files/Thread/netnews_threads.csv'  # Replace with your actual path
+input_csv_path = '/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Thread/netnews_threads.csv'  # Replace with your actual path
 process_csv(input_csv_path)

### 2024-08-25 Scripts - Archive Scraping/thread_scraper.py

@@ -29,7 +29,7 @@ def main():
     csv_filename = f"{newsgroup}_threads.csv"
 
     # Ensure the output directory exists
-    output_directory = '/Users/emerson/Github/usenet_early_histories_project/CSV Files/Threads'
+    output_directory = '/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads'
     os.makedirs(output_directory, exist_ok=True)
 
     # Determine the full output file path

### 2024-08-25 Scripts - Data Cleaning and Visuals/_CSV Cleaning.Rmd
changed directory locations and such
fixed directories in code

--- 2024-08-25 Scripts - Data Cleaning and Visualizations/CSV Cleaning.Rmd
@@
 rm(list = ls()) 
-setwd("/Users/emerson/Github/Usenet")
+setwd("/Users/emerson/Github/usenet_AIDs_discourses_webpage")
 ```
@@
 # Load Directories
-threads_directory <- "CSV Files/Threads"
-comments_directory <- "CSV Files/Comments"
+threads_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads/"
+comments_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments/"
 
 # Load the datasets
-all_threads <- read.csv("CSV Files/Threads/combined_threads.csv")
-all_comments <- read.csv("CSV Files/Comments/combined_comments.csv")
+all_threads <- read.csv(file.path(threads_directory, "combined_threads.csv"))
+all_comments <- read.csv(file.path(comments_directory, "combined_comments.csv"))
 

### 2024-08-25 Scripts - Data Cleaning and Visuals/_Webpage Visualizations Code.Rmd
fixed directories in code

--- 2024-08-25 Webpage Visualizations Code.Rmd
@@
 
-```{r R Read and Clean CSVs}
+```{r R Define Directories and Read/Clean CSVs}
 # Load Directories
-threads_directory <- "CSV Files/Threads"
-comments_directory <- "CSV Files/Comments"
+output_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage"
+threads_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads"
+comments_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments"
 
 # Load the datasets
-all_threads <- read.csv("CSV Files/Threads/combined_threads_cleaned.csv")
-all_comments <- read.csv("CSV Files/Comments/combined_comments_cleaned.csv")
+all_threads <- read.csv(file.path(threads_directory, "combined_threads_cleaned.csv"))
+all_comments <- read.csv(file.path(comments_directory, "combined_comments_cleaned.csv"))
 
@@
 ```{python Import necessary Python libraries}
+import os
 import pandas as pd
@@
 
-```{python Python Read CSVs}
-all_comments = pd.read_csv("CSV Files/Comments/comments_cleaned_82TO89.csv")
-all_threads = pd.read_csv("CSV Files/Threads/threads_cleaned_82TO89.csv")
+```{python Python Define Directories and Read CSVs}
+# Define directories
+output_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/"
+threads_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads/"
+comments_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments/"
+
+# Load the datasets with the correct file paths
+all_threads = pd.read_csv(os.path.join(threads_directory, "threads_cleaned_82TO89.csv"))
+all_comments = pd.read_csv(os.path.join(comments_directory, "comments_cleaned_82TO89.csv"))
 ```
@@
 plt.tight_layout()
-plt.savefig('images and tables/distribution_of_comments_per_newsgroup.png')
+plt.savefig(os.path.join(output_directory, "images and tables/distribution_of_comments_per_newsgroup.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/number_of_threads_over_time.png')
+plt.savefig(os.path.join(output_directory, "images and tables/number_of_threads_over_time.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/average_comments_per_thread_by_newsgroup.png')
+plt.savefig(os.path.join(output_directory, "images and tables/average_comments_per_thread_by_newsgroup.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/sentiment_score_distribution_across_all_comments.png')
+plt.savefig(os.path.join(output_directory, "images and tables/sentiment_score_distribution_across_all_comments.png"))
 plt.show()
@@
 # Save the figure
-plt.savefig('images and tables/top_25_most_active_users_by_newsgroup.png')
+plt.savefig(os.path.join(output_directory, "images and tables/top_25_most_active_users_by_newsgroup.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/combined_daily_activity_heatmap.png')
+plt.savefig(os.path.join(output_directory, "images and tables/combined_daily_activity_heatmap.png"))
 plt.show()
@@
 import nltk
+import os
 
@@
 plt.tight_layout()
-plt.savefig('images and tables/word_cloud_all_comments.png')
+plt.savefig(os.path.join(output_directory, "images and tables/word_cloud_all_comments.png"))
 plt.show()
@@
     plt.axis('off')
-    plt.title(f'Most Common Words in {newsgroup}')
+    plt.title(f'Most common words in {newsgroup}')
     plt.tight_layout()
-    plt.savefig(f'images and tables/word_cloud_{newsgroup}.png')
+
+    # Use f-string to save the file with the specific newsgroup name
+    plt.savefig(os.path.join(output_directory, f"images and tables/word_cloud_{newsgroup}.png"))
     plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/growth_of_newsgroups_over_time.png')
+plt.savefig(os.path.join(output_directory, "images and tables/growth_of_newsgroups_over_time.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/author_engagement_scatterplot.png')
+plt.savefig(os.path.join(output_directory, "images and tables/author_engagement_scatterplot.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/sentiment_over_time.png')
+plt.savefig(os.path.join(output_directory, "images and tables/sentiment_over_time.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/sentiment_distribution_by_newsgroup.png')
+plt.savefig(os.path.join(output_directory, "images and tables/sentiment_distribution_by_newsgroup.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/monthly_sentiment_heatmap.png')
+plt.savefig(os.path.join(output_directory, "images and tables/monthly_sentiment_heatmap.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/sentiment_over_time_by_newsgroup.png')
+plt.savefig(os.path.join(output_directory, "images and tables/sentiment_over_time_by_newsgroup.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/sentiment_polarity_distribution.png')
+plt.savefig(os.path.join(output_directory, "images and tables/sentiment_polarity_distribution.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/sentiment_trend_rolling_average.png')
+plt.savefig(os.path.join(output_directory, "images and tables/sentiment_trend_rolling_average.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/word_cloud_positive_sentiment.png')
+0_output_path = os.path.join(output_directory, "images and tables/word_cloud_positive_sentiment.png"))
+plt.savefig(0_output_path)
 plt.show()
@@
 plt.tight_layout()
-plt.savefig('images and tables/word_cloud_negative_sentiment.png')
+plt.savefig(os.path.join(output_directory, "images and tables/word_cloud_negative_sentiment.png"))
 plt.show()
@@
 # Save the network graph to an HTML file with full width and height
-visSave(network_graph, file = "Images and Tables/network_graph.html")
+network_graph_path <- file.path(output_directory, "images and tables/network_graph.html")
+visSave(network_graph, file = network_graph_path)
 
@@
 # Inject the legend into the HTML file
-html_file <- "Images and Tables/network_graph.html"
-html_content <- readLines(html_file)
+html_content <- readLines(network_graph_path)
 html_content <- c(html_content, html_legend)
-writeLines(html_content, html_file)
+writeLines(html_content, network_graph_path)
 ```

### 2024-08-25 Scripts - Data Cleaning and Visuals/_Webpage Visualizations Code.Rmd
fixed directories again

@@
 plt.tight_layout()
-0_output_path = os.path.join(output_directory, "images and tables/word_cloud_positive_sentiment.png"))
+plt.savefig(os.path.join(output_directory, "images and tables/word_cloud_positive_sentiment.png"))
 plt.savefig(0_output_path)

### 2024-08-25 Scripts - Data Cleaning and Visuals/_CSV Cleaning.Rmd
made changes, testing connection

@@
 library(htmltools)
+# Load necessary library
+library(dplyr)
+# Load necessary libraries
+library(ggplot2)
+library(dplyr)
 ```
@@
 ```{r}
-# Load necessary libraries
-library(dplyr)
-
 # Load Directories
-threads_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads/"
-comments_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments/"
+output_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/"
+threads_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads"
+comments_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments"
 
@@
 ```{r}
-# Load necessary libraries
-library(ggplot2)
-library(dplyr)
-
 # Function to clean the datetime strings
@@
 
-# Descriptive Statistics
-
-## Primary
-```{r}
-# Load necessary library
-library(dplyr)
-library(sjPlot)
-
-# Calculate statistics using dplyr
-summary_df <- all_comments %>%
-  group_by(newsgroup) %>%
-  summarize(
-    Threads = n_distinct(Thread.ID),
-    Comments = n(),
-    Authors = n_distinct(Author),
-    Avg_Comments_Per_Thread = Comments / Threads,
-    Avg_Sentiment_Score = mean(SentimentScore, na.rm = TRUE)
-  )
-
-# Add a totals row
-totals <- summary_df %>%
-  summarize(
-    newsgroup = "Total",
-    Threads = sum(Threads),
-    Comments = sum(Comments),
-    Authors = n_distinct(all_comments$Author),
-    Avg_Comments_Per_Thread = sum(Comments) / sum(Threads),
-    Avg_Sentiment_Score = mean(all_comments$SentimentScore, na.rm = TRUE)
-  )
-
-# Combine the summary with the totals row
-summary_df <- bind_rows(summary_df, totals)
-
-# Print the summary data frame with totals
-tab_df(summary_df, file = "Images and Tables/descriptive_statistics_table.html")
-```
-
-```{r}
-library(knitr)
-library(kableExtra)
-
-# Create the table
-summary_table <- kable(summary_df, format = "html", table.attr = "style='width:100%;'") %>%
-  kable_styling(full_width = FALSE) %>%
-  row_spec(0, bold = TRUE) %>%  # Make the first row bold
-  row_spec(nrow(summary_df), hline_after = TRUE)  # Add a line after the second to last row
-
-# Print the table
-summary_table
-```
-
-## Keyword Search Statistics
-```{r}
-# Load necessary library
-library(dplyr)
+# Filter Additionally by Keyword
+```{r Filter by Keyword}
 
@@
 
-## Save Keyword CSVs to File
-```{r}
+```{r Save Keyword CSVs to File}
 # Collect all related threads and comments
@@
 ```
+
+# Table and Figures
+```{r Descriptive Statistics}
+# Load necessary library
+library(dplyr)
+library(sjPlot)
+
+# Calculate statistics using dplyr
+summary_df <- all_comments %>%
+  group_by(newsgroup) %>%
+  summarize(
+    Threads = n_distinct(Thread.ID),
+    Comments = n(),
+    Authors = n_distinct(Author),
+    Avg_Comments_Per_Thread = Comments / Threads,
+    Avg_Sentiment_Score = mean(SentimentScore, na.rm = TRUE)
+  )
+
+# Add a totals row
+totals <- summary_df %>%
+  summarize(
+    newsgroup = "Total",
+    Threads = sum(Threads),
+    Comments = sum(Comments),
+    Authors = n_distinct(all_comments$Author),
+    Avg_Comments_Per_Thread = sum(Comments) / sum(Threads),
+    Avg_Sentiment_Score = mean(all_comments$SentimentScore, na.rm = TRUE)
+  )
+
+# Combine the summary with the totals row
+summary_df <- bind_rows(summary_df, totals)
+
+# Print the summary data frame with totals
+tab_df(summary_df, file = paste0(output_directory, "Images and Tables/descriptive_statistics_table.html"))
+```

### 2024-08-25 Scripts - Data Cleaning and Visuals/_CSV Cleaning.Rmd
cleaned up csv cleaning code

@@
 
-## Loading Libraries
-```{r}
+## Maintenance
+```{r Load LIbraries, Directories, and Datasets}
+# Load Libraries
 library(tidyverse)
@@
 library(htmltools)
-# Load necessary library
-library(dplyr)
-# Load necessary libraries
 library(ggplot2)
 library(dplyr)
-```
-## Read and Clean CSVs
-```{r}
+library(syuzhet)
+library(sjPlot)
+
 # Load Directories
@@
 all_comments <- read.csv(file.path(comments_directory, "combined_comments.csv"))
+```
 
+```{r Dataset Cleaning}
 # Assign unique identifiers to newsgroups
@@
 
-# Display the updated dataframes (optional)
-head(all_threads)
-head(all_comments)
-```
-## Fix Date and Time Columns
-```{r}
 # Function to clean the datetime strings
@@
 all_threads$Date <- as.Date(all_threads$Date, format = "%m/%d/%y")
+
+# Display the updated dataframes (optional)
+head(all_threads)
+head(all_comments)
 ```
 
-## Run and Sentiment Scores
-```{r} 
-library(syuzhet)
+```{r Run and Add Sentiment Scores} 
 all_comments <- all_comments %>% mutate(SentimentScore = get_sentiment(Full.Text, method = "afinn"))
@@
 
-## Save Cleaned CSVs to File
-```{r}
+```{r Save Cleaned CSVs to File}
 write.csv(all_threads, file.path(threads_directory, "combined_threads_cleaned.csv"), row.names = FALSE)
@@
 
-# Filter Additionally by Keyword
+# Additional Filtering
 ```{r Filter by Keyword}
-
 # List of extended keywords and phrases
@@
 ```{r Descriptive Statistics}
-# Load necessary library
-library(dplyr)
-library(sjPlot)
-
 # Calculate statistics using dplyr

### 2024-08-25 Scripts - Data Cleaning and Visuals/_CSV Cleaning.Rmd
cleaned up cleaning code

@@
 
-# Old Read and Merge (DONT RUN)
-netmed_threads <- read.csv("CSV Files/Threads/netmed_threads.csv")
-netmotss_threads <- read.csv("CSV Files/Threads/netmotss_threads.csv")
-netnews_threads <- read.csv("CSV Files/Threads/netnews_threads.csv")
-netpolitics_threads <- read.csv("CSV Files/Threads/netpolitics_threads.csv")
-netreligion_threads <- read.csv("CSV Files/Threads/netreligion_threads.csv")
-netsingles_threads <- read.csv("CSV Files/Threads/netsingles_threads.csv")
+```{r Old Read and Merge, eval=FALSE, include=FALSE}
+netmed_threads <- read.csv(file.path(threads_directory, "netmed_threads.csv")
+netmotss_threads <- read.csv(file.path(threads_directory, "netmotss_threads.csv")
+netnews_threads <- read.csv(file.path(threads_directory, "netnews_threads.csv")
+netpolitics_threads <- read.csv(file.path(threads_directory, "netpolitics_threads.csv")
+netreligion_threads <- read.csv(file.path(threads_directory, "netreligion_threads.csv")
+netsingles_threads <- read.csv(file.path(threads_directory, "netsingles_threads.csv")
 
-netmed_comments <- read.csv("CSV Files/Comments/netmed_comments.csv")
-netmotss_comments <- read.csv("CSV Files/Comments/netmotss_comments.csv")
-netnews_comments <- read.csv("CSV Files/Comments/netnews_comments.csv")
-netpolitics_comments <- read.csv("CSV Files/Comments/netpolitics_comments.csv")
-netreligion_comments <- read.csv("CSV Files/Comments/netreligion_comments.csv")
-netsingles_comments <- read.csv("CSV Files/Comments/netsingles_comments.csv")
+netmed_comments <- read.csv(file.path(comments_directory, "netmed_comments.csv")
+netmotss_comments <- read.csv(file.path(comments_directory, "netmotss_comments.csv")
+netnews_comments <- read.csv(file.path(comments_directory, "netnews_comments.csv")
+netpolitics_comments <- read.csv(file.path(comments_directory, "netpolitics_comments.csv")
+netreligion_comments <- read.csv(file.path(comments_directory, "netreligion_comments.csv")
+netsingles_comments <- read.csv(file.path(comments_directory, "netsingles_comments.csv")
 
@@
 write.csv(all_comments, file.path(comments_directory, "combined_comments.csv"), row.names = FALSE)
----
-
----
+```
 
 # Maintainence
-
-## Reset
-```{r}
+```{r Reset and Set Working Directory}
 rm(list = ls()) 
-setwd("/Users/emerson/Github/usenet_AIDs_discourses_webpage")
+knitr::opts_knit$set(root.dir = '/Users/emerson/Github/usenet_AIDs_discourses_webpage')
 ```
 
-## Maintenance
 ```{r Load LIbraries, Directories, and Datasets}
@@
 
-# Additional Filtering
-```{r Filter by Keyword}
-# List of extended keywords and phrases
-keywords <- c("aids", "hiv", "acquired immune deficiency syndrome", "human immunodeficiency virus",
-              "gay plague", "gay cancer", "kaposi's sarcoma", "pneumocystis pneumonia",
-              "homosexual disease", "gay disease", "gay fear", "fear of gay", "fear of homosexual",
-              "sexual orientation disease")
-
-# Function to flag comments with keywords
-flag_keywords <- function(text) {
-  # Convert text to lowercase
-  text <- tolower(text)
-  # Check if any keyword is present
-  grepl(paste(keywords, collapse = "|"), text)
-}
-
-# Add a column to indicate if the comment contains any keyword
-all_comments <- all_comments %>%
-  mutate(Contains_Keyword = flag_keywords(Full.Text))
-
-# Identify threads with at least one comment containing a keyword
-threads_with_keywords <- all_comments %>%
-  filter(Contains_Keyword) %>%
-  distinct(Thread.ID) %>%
-  pull(Thread.ID)
-
-# Filter comments in threads with at least one keyword
-comments_in_keyword_threads <- all_comments %>%
-  filter(Thread.ID %in% threads_with_keywords)
-
-# Group by newsgroup and calculate required statistics
-keywords_summary_df <- comments_in_keyword_threads %>%
-  group_by(newsgroup) %>%
-  summarize(
-    Comments_with_Keywords = sum(Contains_Keyword),
-    Conversations_Mentioned_In = n_distinct(Thread.ID),
-    Total_Comments_In_Threads = n(),
-    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100
-  )
-
-# Add a totals row
-totals <- keywords_summary_df %>%
-  summarize(
-    newsgroup = "Total",
-    Comments_with_Keywords = sum(Comments_with_Keywords),
-    Conversations_Mentioned_In = sum(Conversations_Mentioned_In),
-    Total_Comments_In_Threads = sum(Total_Comments_In_Threads),
-    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100
-  )
-
-# Combine the summary with the totals row
-keywords_summary_df <- bind_rows(keywords_summary_df, totals)
-
-# Print the keyword summary data frame with totals
-print(keywords_summary_df)
-```
-
-```{r Save Keyword CSVs to File}
-# Collect all related threads and comments
-related_threads <- all_threads %>%
-  filter(Unique_ThreadID %in% threads_with_keywords) %>%
-  filter(Date <= as.Date("1988-12-31"))
-
-related_comments <- all_comments %>%
-  filter(Thread.ID %in% threads_with_keywords) %>%
-  filter(Date <= as.Date("1988-12-31"))
-
-# Write the related threads and comments to CSV files
-write.csv(related_threads, file.path(threads_directory, "aids_related_threads.csv"), row.names = FALSE)
-write.csv(related_comments, file.path(comments_directory, "aids_related_comments.csv"), row.names = FALSE)
-```
-
 # Table and Figures
@@
 # Print the summary data frame with totals
-tab_df(summary_df, file = paste0(output_directory, "Images and Tables/descriptive_statistics_table.html"))
+tab_df(summary_df, file = paste0(output_directory, "images and tables/descriptive_statistics_table.html"))
 ```
+
+# Additional Filtering
+```{r Filter by Keyword and Add Relevancy Scores}
+# List of refined keywords and phrases (broad keywords removed)
+keywords <- c("aids", "htlv", "hiv", "acquired immune deficiency syndrome", "human immunodeficiency virus",
+              "gay plague", "gay cancer", "kaposi's sarcoma", "pneumocystis pneumonia",
+              "homosexual disease", "gay disease", "gay fear", "fear of gay", "fear of homosexual",
+              "sexual orientation disease", "virus", "sex", "promiscuity", "patients")
+
+# Function to calculate relevancy score
+calculate_relevancy <- function(text) {
+  # Convert text to lowercase
+  text <- tolower(text)
+  # Check for the presence of each keyword
+  keyword_matches <- sapply(keywords, function(keyword) grepl(keyword, text))
+  # Calculate relevancy score as the number of keywords present
+  relevancy_score <- sum(keyword_matches)
+  return(relevancy_score)
+}
+
+# Step 1: Identify threads with at least one comment containing a keyword
+all_comments_aids <- all_comments %>%
+  rowwise() %>%
+  mutate(Contains_Keyword = any(sapply(keywords, function(keyword) grepl(keyword, tolower(Full.Text)))))
+
+# Filter threads containing at least one keyword
+all_threads_aids <- all_comments_aids %>%
+  filter(Contains_Keyword) %>%
+  distinct(Thread.ID)
+
+# Step 2: Fetch all comments from threads with at least one keyword-containing comment
+comments_in_keyword_threads <- all_comments %>%
+  filter(Thread.ID %in% all_threads_aids$Thread.ID)
+
+# Step 3: Calculate relevancy score for each comment and add it to the dataframe
+comments_in_keyword_threads <- comments_in_keyword_threads %>%
+  rowwise() %>%
+  mutate(Relevancy = calculate_relevancy(Full.Text))
+
+# Save the comments dataframe to CSV
+write.csv(comments_in_keyword_threads, file.path(comments_directory, "aids_related_comments.csv"), row.names = FALSE)
+
+# Step 4: Calculate the average relevancy score for each thread
+thread_relevancy_scores <- comments_in_keyword_threads %>%
+  group_by(Thread.ID) %>%
+  summarize(Thread_Relevancy = mean(Relevancy, na.rm = TRUE))
+
+# Merge thread relevancy scores back to thread-level dataframe
+threads_summary_df <- comments_in_keyword_threads %>%
+  distinct(Thread.ID, newsgroup) %>%
+  left_join(thread_relevancy_scores, by = "Thread.ID")
+
+# Save the threads dataframe to CSV
+write.csv(threads_summary_df, file.path(threads_directory, "aids_related_threads.csv"), row.names = FALSE)
+```
+
+```{r Keyword Descriptive Statistics}
+# Step 5: Group by newsgroup and calculate required statistics, including thread relevancy
+keywords_summary_df <- comments_in_keyword_threads %>%
+  group_by(newsgroup) %>%
+  summarize(
+    Comments_with_Keywords = sum(Relevancy > 0),
+    Conversations_Mentioned_In = n_distinct(Thread.ID),
+    Total_Comments_In_Threads = n(),
+    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100,
+    Average_Relevancy_Score = mean(Relevancy, na.rm = TRUE)
+  )
+
+# Merge thread relevancy averages back to the summary dataframe
+threads_summary_df_grouped <- threads_summary_df %>%
+  group_by(newsgroup) %>%
+  summarize(Average_Thread_Relevancy = mean(Thread_Relevancy, na.rm = TRUE))
+
+# Combine comment and thread summaries
+keywords_summary_df <- keywords_summary_df %>%
+  left_join(threads_summary_df_grouped, by = "newsgroup")
+
+# Add a totals row
+totals <- keywords_summary_df %>%
+  summarize(
+    newsgroup = "Total",
+    Comments_with_Keywords = sum(Comments_with_Keywords),
+    Conversations_Mentioned_In = sum(Conversations_Mentioned_In),
+    Total_Comments_In_Threads = sum(Total_Comments_In_Threads),
+    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100,
+    Average_Relevancy_Score = mean(Average_Relevancy_Score, na.rm = TRUE),
+    Average_Thread_Relevancy = mean(Average_Thread_Relevancy, na.rm = TRUE)
+  )
+
+# Combine the summary with the totals row
+keywords_summary_df <- bind_rows(keywords_summary_df, totals)
+
+# Print the keyword summary data frame with totals
+tab_df(keywords_summary_df, file = paste0(output_directory, "images and tables/aids_descriptive_statistics_table.html"))
+```

### 2024-08-25 Scripts - Data Cleaning and Visuals/_CSV Cleaning.Rmd
did some more cleaning

@@
 
-```{r Load LIbraries, Directories, and Datasets}
+```{r Load Libraries, Directories, and Datasets}
 # Load Libraries
@@
 
-# Merge thread relevancy scores back to thread-level dataframe
-threads_summary_df <- comments_in_keyword_threads %>%
-  distinct(Thread.ID, newsgroup) %>%
-  left_join(thread_relevancy_scores, by = "Thread.ID")
+# Merge thread relevancy scores with the original all_threads dataframe and filter to keep only relevant threads
+threads_summary_df <- all_threads %>%
+  filter(Unique_ThreadID %in% all_threads_aids$Thread.ID) %>%
+  left_join(thread_relevancy_scores, by = c("Unique_ThreadID" = "Thread.ID"))
 

### 2024-08-25 Scripts - Data Cleaning and Visuals/_Webpage Visualizations Code.Rmd
did some more cleaning

@@
 
-# Maintenance and Cleaning
+# Maintenance for R and Python
 ```{r Reset and Setup}
@@
 
-```{r Import necessary R libraries}
-# Load all necessary libraries at once
+```{r R Load Libraries, Directories, and Datasets}
 library(tidyverse)
@@
 library(topicmodels)
-```
+library(visNetwork)
+library(RColorBrewer)
 
-```{r R Define Directories and Read/Clean CSVs}
 # Load Directories
@@
 # Load the datasets
-all_threads <- read.csv(file.path(threads_directory, "combined_threads_cleaned.csv"))
-all_comments <- read.csv(file.path(comments_directory, "combined_comments_cleaned.csv"))
+all_threads <- read.csv(file.path(threads_directory, "aids_related_threads.csv"))
+all_comments <- read.csv(file.path(comments_directory, "aids_related_comments.csv"))
+```
 
+```{python Python Load Libraries, Directories, and Datasets}
+import os
+import pandas as pd
+import matplotlib.pyplot as plt
+import seaborn as sns
+import numpy as np
+import plotly.express as px
+import plotly.graph_objects as go
+import networkx as nx
+import scipy
+
+# Define directories
+output_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/"
+threads_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads/"
+comments_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments/"
+
+# Load the datasets with the correct file paths
+all_threads = pd.read_csv(os.path.join(threads_directory, "threads_cleaned_82TO89.csv"))
+all_comments = pd.read_csv(os.path.join(comments_directory, "comments_cleaned_82TO89.csv"))
+```
+
+```{r R CSV Cleaning}
 all_threads <- all_threads %>% drop_na()
@@
 
-```{python Import necessary Python libraries}
-import os
-import pandas as pd
-import matplotlib.pyplot as plt
-import seaborn as sns
-import numpy as np
-import plotly.express as px
-import plotly.graph_objects as go
-import networkx as nx
-import scipy
-```
-
-```{python Python Define Directories and Read CSVs}
-# Define directories
-output_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/"
-threads_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads/"
-comments_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments/"
-
-# Load the datasets with the correct file paths
-all_threads = pd.read_csv(os.path.join(threads_directory, "threads_cleaned_82TO89.csv"))
-all_comments = pd.read_csv(os.path.join(comments_directory, "comments_cleaned_82TO89.csv"))
-```
-
-# Initial Visualizations
+# Initial Visualizations - Python
 ```{python Distribution of Comments per Newsgroup}
@@
 
-# Sentiment Visualizations
+# Sentiment Visualizations - Python
 ```{python Average Sentiment Over Time Across All Newsgroups}
@@
 
-# Network Visualizations
-```{r Load R Libraries}
-# Load necessary libraries
-library(dplyr)
-library(tidyr)
-library(visNetwork)
-library(igraph)  # Needed for community detection
-library(RColorBrewer)  # For generating pastel colors
-```
-
+# Network Visualizations - R
 ```{r Get Authors Metadata}

### 2024-08-28 menu.js
added js

@@ -1,0 +1,29 @@
+// menu.js
+
+// Function to load external HTML files into a container
+function loadHTML(containerId, url) {
+    fetch(url)
+        .then(response => response.text())
+        .then(data => {
+            document.getElementById(containerId).innerHTML = data;
+
+            // Reattach the script to ensure it runs after loading
+            var script = document.createElement('script');
+            script.textContent = `
+                function toggleMenu() {
+                    var menu = document.getElementById('menuItems');
+                    if (menu.style.display === 'block') {
+                        menu.style.display = 'none';
+                    } else {
+                        menu.style.display = 'block';
+                    }
+                }
+            `;
+            document.body.appendChild(script);
+        });
+}
+
+// Load the menu when the page loads
+document.addEventListener('DOMContentLoaded', function() {
+    loadHTML('menu-container', 'menu.html');
+});

### 2024-08-28 menu.js
updated js

@@ -7,23 +7,26 @@ function loadHTML(containerId, url) {
         .then(data => {
             document.getElementById(containerId).innerHTML = data;
 
-            // Reattach the script to ensure it runs after loading
-            var script = document.createElement('script');
-            script.textContent = `
-                function toggleMenu() {
-                    var menu = document.getElementById('menuItems');
-                    if (menu.style.display === 'block') {
-                        menu.style.display = 'none';
-                    } else {
-                        menu.style.display = 'block';
+            // If loading the menu, reattach the script to ensure it runs
+            if (url === 'menu.html') {
+                var script = document.createElement('script');
+                script.textContent = `
+                    function toggleMenu() {
+                        var menu = document.getElementById('menuItems');
+                        if (menu.style.display === 'block') {
+                            menu.style.display = 'none';
+                        } else {
+                            menu.style.display = 'block';
+                        }
                     }
-                }
-            `;
-            document.body.appendChild(script);
+                `;
+                document.body.appendChild(script);
+            }
         });
 }
 
-// Load the menu when the page loads
+// Load the header and menu when the page loads
 document.addEventListener('DOMContentLoaded', function() {
+    loadHTML('header-container', 'header.html');
     loadHTML('menu-container', 'menu.html');
 });

### 2024-08-28 menu.js
trying again with menu

@@ -1,5 +1,3 @@
-// menu.js
-
 // Function to load external HTML files into a container
 function loadHTML(containerId, url) {
     fetch(url)
@@ -7,8 +5,8 @@ function loadHTML(containerId, url) {
         .then(data => {
             document.getElementById(containerId).innerHTML = data;
 
-            // If loading the menu, reattach the script to ensure it runs
-            if (url === 'menu.html') {
+            // Reattach the script to ensure it runs if the loaded content has scripts
+            if (containerId === 'menu-container') {
                 var script = document.createElement('script');
                 script.textContent = `
                     function toggleMenu() {
@@ -25,8 +23,6 @@ function loadHTML(containerId, url) {
         });
 }
 
-// Load the header and menu when the page loads
-document.addEventListener('DOMContentLoaded', function() {
-    loadHTML('header-container', 'header.html');
-    loadHTML('menu-container', 'menu.html');
-});
+// Load the header and menu
+loadHTML('header-container', 'header.html');
+loadHTML('menu-container', 'menu.html');

### 2024-08-28 menu.js
trying again smh

@@ -23,6 +23,7 @@ function loadHTML(containerId, url) {
         });
 }
 
-// Load the header and menu
+// Load the header, menu, and buttons
 loadHTML('header-container', 'header.html');
 loadHTML('menu-container', 'menu.html');
+loadHTML('buttons-container', 'buttons.html');

### 2024-08-28 menu.js
removing buttons

@@ -26,4 +26,3 @@ function loadHTML(containerId, url) {
 // Load the header, menu, and buttons
 loadHTML('header-container', 'header.html');
 loadHTML('menu-container', 'menu.html');
-loadHTML('buttons-container', 'buttons.html');

### 2024-09-01 Scripts - Data Cleaning and Visuals/_CSV Cleaning.Rmd
added data

@@
   summarize(
+    Unique_Authors = n_distinct(Author),
     Comments_with_Keywords = sum(Relevancy > 0),
@@
     Total_Comments_In_Threads = sum(Total_Comments_In_Threads),
+    Unique_Authors = sum(Unique_Authors),
     Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100,

### 2024-09-01 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
testing

--- 2024-08-25 Scripts - Data Cleaning and Visuals/_Webpage Visualizations Code.Rmd
@@
 ---
-title: "Web Page Visualization Code"
+title: "Paper Visualization"
 author: "Emerson Johnston"
-lastmodifeddate: "2024-08-24"
+lastmodifeddate: "2024-09-01"
 output:
@@
 # Load the datasets
-all_threads <- read.csv(file.path(threads_directory, "aids_related_threads.csv"))
-all_comments <- read.csv(file.path(comments_directory, "aids_related_comments.csv"))
+all_threads <- read.csv(file.path(threads_directory, "aids_related_threads_82TO86.csv"))
+all_comments <- read.csv(file.path(comments_directory, "aids_related_comments_82TO86.csv"))
+```
+
+```{r R CSV Cleaning}
+all_threads <- all_threads %>% drop_na()
+all_comments <- all_comments %>% drop_na()
+all_comments$Date <- as.Date(all_comments$Date, format = "%Y-%m-%d")
+all_threads$Date <- as.Date(all_threads$Date, format = "%Y-%m-%d")
 ```
@@
 # Load the datasets with the correct file paths
-all_threads = pd.read_csv(os.path.join(threads_directory, "threads_cleaned_82TO89.csv"))
-all_comments = pd.read_csv(os.path.join(comments_directory, "comments_cleaned_82TO89.csv"))
+all_threads = pd.read_csv(os.path.join(threads_directory, "aids_related_threads_82TO86.csv"))
+all_comments = pd.read_csv(os.path.join(comments_directory, "aids_related_comments_82TO86.csv"))
 ```
 
-```{r R CSV Cleaning}
-all_threads <- all_threads %>% drop_na()
-all_comments <- all_comments %>% drop_na()
+# Theme Prevelance Hypothesis
 
-# Ensure the 'Date' columns are properly formatted as Date objects
-all_comments$Date <- as.Date(all_comments$Date, format = "%Y-%m-%d")
-all_threads$Date <- as.Date(all_threads$Date, format = "%Y-%m-%d")
+# Emotional Tone Hypothesis
 
-# Filter the datasets to include only data before January 1, 1989
-all_comments <- all_comments %>%
-  filter(Date < as.Date("1989-01-01")) %>% filter(Date > as.Date("1982-01-01"))
-
-all_threads <- all_threads %>%
-  filter(Date < as.Date("1989-01-01")) %>% filter(Date > as.Date("1982-01-01"))
-
-write.csv(all_threads, file.path(threads_directory, "threads_cleaned_82TO89.csv"), row.names = FALSE)
-write.csv(all_comments, file.path(comments_directory, "comments_cleaned_82TO89.csv"), row.names = FALSE)
-```
-
-# Initial Visualizations - Python
-```{python Distribution of Comments per Newsgroup}
-plt.figure(figsize=(10, 6))
-sns.countplot(data=all_comments, x='newsgroup', order=all_comments['newsgroup'].value_counts().index)
-plt.title('Distribution of Comments per Newsgroup')
-plt.xticks(rotation=45)
-plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/distribution_of_comments_per_newsgroup.png"))
-plt.show()
-```
-
-```{python Number of Threads Over Time}
-all_threads['Date'] = pd.to_datetime(all_threads['Date'])
-
-plt.figure(figsize=(10, 6))
-all_threads.groupby(all_threads['Date'].dt.to_period('M')).size().plot(kind='line')
-plt.title('Number of Threads Across All Newsgroups Over Time')
-plt.xlabel('Month')
-plt.ylabel('Number of Threads')
-plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/number_of_threads_over_time.png"))
-plt.show()
-```
-
-```{python Average Number of Comments per Thread by Newsgroup}
-avg_comments_per_thread = all_threads.groupby('newsgroup')['Number.of.Messages'].mean().reset_index()
-
-plt.figure(figsize=(10, 6))
-sns.barplot(data=avg_comments_per_thread, x='newsgroup', y='Number.of.Messages', order=avg_comments_per_thread.sort_values('Number.of.Messages', ascending=False)['newsgroup'])
-plt.title('Average Number of Comments per Thread by Newsgroup')
-plt.xlabel('Newsgroup')
-plt.ylabel('Average Number of Comments')
-plt.xticks(rotation=45)
-plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/average_comments_per_thread_by_newsgroup.png"))
-plt.show()
-```
-
-```{python Sentiment Score Distribution Across All Comments}
-plt.figure(figsize=(10, 6))
-sns.histplot(all_comments['SentimentScore'], bins=30, kde=True)
-plt.title('Sentiment Score Distribution Across All Comments')
-plt.xlabel('Sentiment Score')
-plt.ylabel('Frequency')
-plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/sentiment_score_distribution_across_all_comments.png"))
-plt.show()
-```
-
-```{python Top 25 Most Active Users}
-import pandas as pd
-import matplotlib.pyplot as plt
-import seaborn as sns
-
-# Get the top 25 authors by the number of comments
-top_authors = all_comments['Author'].value_counts().head(25).index
-
-# Filter the dataset to include only the top 25 authors
-top_authors_data = all_comments[all_comments['Author'].isin(top_authors)]
-
-# Calculate the number of comments by each of the top 25 authors in each newsgroup
-comments_per_newsgroup = top_authors_data.groupby(['Author', 'newsgroup']).size().unstack(fill_value=0)
-
-# Sort authors by total number of comments in descending order
-comments_per_newsgroup['Total Comments'] = comments_per_newsgroup.sum(axis=1)
-comments_per_newsgroup = comments_per_newsgroup.sort_values('Total Comments', ascending=True)
-
-# Remove the 'Total Comments' column for plotting
-comments_per_newsgroup = comments_per_newsgroup.drop(columns='Total Comments')
-
-# Define a distinct color palette for newsgroups
-distinct_colors = sns.color_palette('tab20', len(comments_per_newsgroup.columns))
-
-# Plot a stacked bar plot without white lines between colors and with distinct colors
-comments_per_newsgroup.plot(kind='barh', stacked=True, figsize=(12, 8), color=distinct_colors, edgecolor='none')
-
-plt.title('Top 25 Most Active Users by Newsgroup')
-plt.xlabel('Number of Comments')
-plt.ylabel('Author')
-plt.legend(title='Newsgroup', bbox_to_anchor=(1.05, 1), loc='upper left')
-plt.tight_layout()
-
-# Save the figure
-plt.savefig(os.path.join(output_directory, "images and tables/top_25_most_active_users_by_newsgroup.png"))
-plt.show()
-```
-
-```{python Temporal Heatmap of Daily Activity by Newsgroup}
-import pandas as pd
-import matplotlib.pyplot as plt
-import seaborn as sns
-
-# Convert 'Date.and.Time' to datetime and handle errors
-all_comments['Date.and.Time'] = pd.to_datetime(all_comments['Date.and.Time'], errors='coerce')
-
-# Check if there are any conversion issues and drop those rows
-all_comments = all_comments.dropna(subset=['Date.and.Time'])
-
-# Extract day of the week and hour
-all_comments['DayOfWeek'] = all_comments['Date.and.Time'].dt.day_name()
-all_comments['Hour'] = all_comments['Date.and.Time'].dt.hour
-
-# Group data by DayOfWeek and Hour for all newsgroups combined
-activity_data = all_comments.groupby(['DayOfWeek', 'Hour']).size().reset_index(name='Activity')
-
-# Pivot table to prepare data for heatmap
-heatmap_data = activity_data.pivot_table(index='Hour', columns='DayOfWeek', values='Activity', fill_value=0)
-
-# Reorder days of the week for consistent display
-day_order = ['Monday', 'Tuesday', 'Wednesday', 'Thursday', 'Friday', 'Saturday', 'Sunday']
-heatmap_data = heatmap_data[day_order]
-
-# Create the heatmap
-plt.figure(figsize=(12, 8))
-sns.heatmap(heatmap_data, cmap='viridis')
-plt.title('Daily Activity Heatmap Across All Newsgroups')
-plt.xlabel('Day of Week')
-plt.ylabel('Hour of Day')
-plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/combined_daily_activity_heatmap.png"))
-plt.show()
-```
-
-```{python Word Clouds!}
-import pandas as pd
-from wordcloud import WordCloud
-import matplotlib.pyplot as plt
-from nltk.corpus import stopwords
-import nltk
-import os
-
-# Ensure NLTK stopwords are downloaded
-nltk.download('stopwords')
-stop_words = set(stopwords.words('english'))
-
-# Combine all text data into one string for all comments
-all_text = " ".join(all_comments['Full.Text'].dropna())
-
-# Create word cloud for all comments
-wordcloud_all = WordCloud(width=800, height=400, background_color='white', stopwords=stop_words, collocations=False).generate(all_text)
-
-plt.figure(figsize=(10, 6))
-plt.imshow(wordcloud_all, interpolation='bilinear')
-plt.axis('off')
-plt.title('Most Common Words in All Usenet Comments')
-plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/word_cloud_all_comments.png"))
-plt.show()
-
-# Generate word clouds by newsgroup
-for newsgroup in all_comments['newsgroup'].unique():
-    # Filter comments for the current newsgroup
-    group_text = " ".join(all_comments[all_comments['newsgroup'] == newsgroup]['Full.Text'].dropna())
-
-    # Create word cloud for the specific newsgroup
-    wordcloud_group = WordCloud(width=800, height=400, background_color='white', stopwords=stop_words, collocations=False).generate(group_text)
-
-    plt.figure(figsize=(10, 6))
-    plt.imshow(wordcloud_group, interpolation='bilinear')
-    plt.axis('off')
-    plt.title(f'Most common words in {newsgroup}')
-    plt.tight_layout()
-
-    # Use f-string to save the file with the specific newsgroup name
-    plt.savefig(os.path.join(output_directory, f"images and tables/word_cloud_{newsgroup}.png"))
-    plt.show()
-```
-
-```{python Growth of Newsgroups Over Time}
-# Convert Date to datetime format
-all_threads['Date'] = pd.to_datetime(all_threads['Date'])
-
-# Calculate cumulative count of newsgroups created over time
-plt.figure(figsize=(10, 6))
-all_threads.groupby(all_threads['Date'].dt.to_period('M')).newsgroup.nunique().cumsum().plot(kind='line')
-plt.title('Growth of Newsgroups Over Time')
-plt.xlabel('Month')
-plt.ylabel('Cumulative Number of Newsgroups')
-plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/growth_of_newsgroups_over_time.png"))
-plt.show()
-```
-
-```{python Author Engagement Scatter Plot}
-# Calculate number of comments and threads per author
-author_stats = all_comments.groupby('Author').agg({'Thread.ID': pd.Series.nunique, 'Unique_CommentID': 'count'}).reset_index()
-author_stats.columns = ['Author', 'Threads_Initiated', 'Comments_Made']
-
-plt.figure(figsize=(10, 6))
-sns.scatterplot(data=author_stats, x='Threads_Initiated', y='Comments_Made', alpha=0.6)
-plt.title('Author Engagement: Comments Made vs. Threads Initiated')
-plt.xlabel('Number of Threads Initiated')
-plt.ylabel('Number of Comments Made')
-plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/author_engagement_scatterplot.png"))
-plt.show()
-```
-
-# Sentiment Visualizations - Python
-```{python Average Sentiment Over Time Across All Newsgroups}
-import pandas as pd
-import matplotlib.pyplot as plt
-
-# Ensure 'Date' is in datetime format
-all_comments['Date'] = pd.to_datetime(all_comments['Date'])
-
-# Group by month and calculate average sentiment
-sentiment_over_time = all_comments.groupby(all_comments['Date'].dt.to_period('M'))['SentimentScore'].mean().reset_index()
-sentiment_over_time['Date'] = sentiment_over_time['Date'].dt.to_timestamp()
-
-plt.figure(figsize=(12, 6))
-plt.plot(sentiment_over_time['Date'], sentiment_over_time['SentimentScore'], marker='o', linestyle='-')
-plt.title('Average Sentiment Over Time Across All Newsgroups')
-plt.xlabel('Date')
-plt.ylabel('Average Sentiment Score')
-plt.xticks(rotation=45)
-plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/sentiment_over_time.png"))
-plt.show()
-```
-
-```{python Sentiment Distribution by Newsgroup Boxplot}
-import seaborn as sns
-
-plt.figure(figsize=(12, 6))
-sns.boxplot(x='newsgroup', y='SentimentScore', data=all_comments)
-plt.title('Sentiment Distribution by Newsgroup')
-plt.xlabel('Newsgroup')
-plt.ylabel('Sentiment Score')
-plt.xticks(rotation=45)
-plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/sentiment_distribution_by_newsgroup.png"))
-plt.show()
-```
-
-```{python Monthly Sentiment Heatmap by Newsgroup}
-# Group by newsgroup and month to calculate average sentiment
-monthly_sentiment = all_comments.groupby([all_comments['Date'].dt.to_period('M'), 'newsgroup'])['SentimentScore'].mean().reset_index()
-monthly_sentiment['Date'] = monthly_sentiment['Date'].dt.to_timestamp()
-
-# Pivot table for heatmap
-heatmap_data = monthly_sentiment.pivot('newsgroup', 'Date', 'SentimentScore')
-
-plt.figure(figsize=(12, 8))
-sns.heatmap(heatmap_data, cmap='coolwarm', center=0)
-plt.title('Monthly Sentiment Heatmap by Newsgroup')
-plt.xlabel('Month')
-plt.ylabel('Newsgroup')
-plt.xticks(rotation=45)
-plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/monthly_sentiment_heatmap.png"))
-plt.show()
-```
-
-```{python Sentiment Score Over Time by Newsgroup}
-import pandas as pd
-import matplotlib.pyplot as plt
-import seaborn as sns
-
-# Ensure 'Date' is in datetime format
-all_comments['Date'] = pd.to_datetime(all_comments['Date'])
-
-# Group by month and newsgroup to calculate average sentiment
-sentiment_by_newsgroup = all_comments.groupby([all_comments['Date'].dt.to_period('M'), 'newsgroup'])['SentimentScore'].mean().reset_index()
-sentiment_by_newsgroup['Date'] = sentiment_by_newsgroup['Date'].dt.to_timestamp()
-
-plt.figure(figsize=(14, 8))
-sns.lineplot(data=sentiment_by_newsgroup, x='Date', y='SentimentScore', hue='newsgroup', marker='o')
-plt.title('Average Sentiment Over Time by Newsgroup')
-plt.xlabel('Date')
-plt.ylabel('Average Sentiment Score')
-plt.xticks(rotation=45)
-plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/sentiment_over_time_by_newsgroup.png"))
-plt.show()
-```
-
-```{python Sentiment Polarity Distribution (Positive vs. Negative)}
-# Define positive and negative sentiment based on threshold
-positive_threshold = 0
-all_comments['SentimentPolarity'] = all_comments['SentimentScore'].apply(lambda x: 'Positive' if x > positive_threshold else 'Negative')
-
-plt.figure(figsize=(8, 6))
-sns.countplot(data=all_comments, x='SentimentPolarity', palette=['red', 'green'])
-plt.title('Sentiment Polarity Distribution')
-plt.xlabel('Sentiment Polarity')
-plt.ylabel('Number of Comments')
-plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/sentiment_polarity_distribution.png"))
-plt.show()
-```
-
-```{python Sentiment Trend Analysis with Rolling Average}
-# Calculate rolling average of sentiment over time
-all_comments['RollingSentiment'] = all_comments['SentimentScore'].rolling(window=30, min_periods=1).mean()
-
-plt.figure(figsize=(12, 6))
-plt.plot(all_comments['Date'], all_comments['RollingSentiment'], color='purple')
-plt.title('Sentiment Trend Analysis with Rolling Average')
-plt.xlabel('Date')
-plt.ylabel('Rolling Average Sentiment Score (30-day window)')
-plt.xticks(rotation=45)
-plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/sentiment_trend_rolling_average.png"))
-plt.show()
-```
-
-```{python Top Words Associated with Positive and Negative Sentiments}
-from wordcloud import WordCloud
-
-# Separate positive and negative comments
-positive_comments = " ".join(all_comments[all_comments['SentimentPolarity'] == 'Positive']['Full.Text'].dropna())
-negative_comments = " ".join(all_comments[all_comments['SentimentPolarity'] == 'Negative']['Full.Text'].dropna())
-
-# Create word cloud for positive sentiment
-wordcloud_positive = WordCloud(width=800, height=400, background_color='white', stopwords=stop_words, collocations=False).generate(positive_comments)
-
-plt.figure(figsize=(10, 6))
-plt.imshow(wordcloud_positive, interpolation='bilinear')
-plt.axis('off')
-plt.title('Top Words in Positive Sentiment Comments')
-plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/word_cloud_positive_sentiment.png"))
-plt.savefig(0_output_path)
-plt.show()
-
-# Create word cloud for negative sentiment
-wordcloud_negative = WordCloud(width=800, height=400, background_color='white', stopwords=stop_words, collocations=False).generate(negative_comments)
-
-plt.figure(figsize=(10, 6))
-plt.imshow(wordcloud_negative, interpolation='bilinear')
-plt.axis('off')
-plt.title('Top Words in Negative Sentiment Comments')
-plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/word_cloud_negative_sentiment.png"))
-plt.show()
-```
-
-# Network Visualizations - R
-```{r Get Authors Metadata}
-# Step 1: Calculate basic metadata for each author
-metadata <- all_comments %>%
-  group_by(Author) %>%
-  summarize(
-    total_threads = n_distinct(Thread.ID),  # Count distinct threads per author
-    total_comments = n(),  # Total number of comments made by the author
-    threads_started = sum(Thread_Relative_CommentID == "CM00001", na.rm = TRUE),  # Number of threads started by the author
-    .groups = 'drop'
-  )
-
-# Step 2: Calculate comments per newsgroup for each author
-comments_per_newsgroup <- all_comments %>%
-  group_by(Author, newsgroup) %>%
-  summarize(total_comments_in_newsgroup = n(), .groups = 'drop')
-
-# Step 3: Pivot the newsgroup data to wide format to create separate columns for each newsgroup
-comments_per_newsgroup_wide <- comments_per_newsgroup %>%
-  pivot_wider(
-    names_from = newsgroup,
-    values_from = total_comments_in_newsgroup,
-    values_fill = list(total_comments_in_newsgroup = 0)  # Fill missing values with 0
-  )
-
-# Step 4: Merge the metadata with the wide format newsgroup data
-metadata <- metadata %>%
-  left_join(comments_per_newsgroup_wide, by = "Author")
-
-# Step 5: Calculate author influence based on the number of connections in the network
-# Calculate the degree (number of connections) for each author in the graph
-edges <- all_comments %>%
-  filter(Thread.ID != "") %>%
-  group_by(Thread.ID) %>%
-  filter(n() > 1) %>%
-  summarize(edgelist = list(combn(Author, 2, simplify = FALSE))) %>%
-  unnest(edgelist) %>%
-  unnest_wider(edgelist, names_sep = "") %>%
-  rename(source = edgelist1, target = edgelist2) %>%
-  filter(source != target) %>%
-  group_by(source, target) %>%
-  summarize(weight = n(), .groups = 'drop')
-
-# Create graph object
-graph <- igraph::graph_from_data_frame(edges, directed = FALSE)
-
-# Calculate the degree for each author as their influence
-author_influence <- data.frame(
-  Author = igraph::V(graph)$name,
-  influence = igraph::degree(graph)
-)
-
-# Step 6: Merge author influence into metadata
-metadata <- metadata %>%
-  left_join(author_influence, by = "Author")
-
-# Step 7: Perform community detection using Louvain algorithm
-communities <- cluster_louvain(graph)
-membership <- membership(communities)
-
-# Step 8: Create node_communities DataFrame
-node_communities <- data.frame(
-  name = V(graph)$name,  # Node names (authors)
-  community = membership  # Community assignment
-)
-
-# Step 9: Sort the metadata DataFrame by total_comments in descending order
-metadata <- metadata %>%
-  arrange(desc(total_comments))
-
-# Preview the updated metadata dataframe
-print(metadata)
-print(node_communities)  # Display node communities
-```
-
-```{r Create Edges and Nodes}
-# Create top_authors list for the top 15 authors by influence
-top_authors <- metadata %>%
-  arrange(desc(influence)) %>%
-  slice(1:20) %>%
-  pull(Author)
-
-# Filter metadata and comments data for only top authors
-metadata <- metadata %>%
-  filter(Author %in% top_authors)
-
-comments_per_newsgroup_wide <- comments_per_newsgroup_wide %>%
-  filter(Author %in% top_authors)
-
-# Step 10: Create Edges and Nodes for the visualization
-
-# Filter edges to include only those involving top authors
-edges <- edges %>%
-  filter(source %in% top_authors & target %in% top_authors)
-
-# Prepare nodes data
-nodes <- data.frame(
-  name = top_authors,
-  size = author_influence$influence[match(top_authors, author_influence$Author)],
-  label = top_authors
-)
-
-# Merge nodes with their community data
-nodes <- nodes %>%
-  left_join(node_communities, by = "name")
-
-# Add metadata and newsgroup comments in descending order to the title
-nodes <- nodes %>%
-  mutate(
-    # Calculate the newsgroup comments section dynamically
-    comments_per_newsgroup = sapply(name, function(author_name) {
-      author_data <- comments_per_newsgroup_wide %>%
-        filter(Author == author_name) %>%
-        select(-Author) %>%
-        pivot_longer(cols = everything(), names_to = "newsgroup", values_to = "comments") %>%
-        arrange(desc(comments))
-
-      paste(author_data$newsgroup, author_data$comments, sep = ": ", collapse = "<br>")
-    }),
-
-    # Prepare the title with the formatted metadata and comments per newsgroup
-    title = paste0(
-      "<div style='background-color: #f2f2f2; border: 2px solid #666666; padding: 5px;'>",  # Custom tooltip styling
-      "<strong>", name, "</strong><br>",
-      "Total Threads Participated: ", metadata$total_threads[match(name, metadata$Author)], "<br>",
-      "Total Comments: ", metadata$total_comments[match(name, metadata$Author)], "<br>",
-      "Threads Started: ", metadata$threads_started[match(name, metadata$Author)], "<br>",
-      "Influence: ", metadata$influence[match(name, metadata$Author)], " (based on the number of connections)", "<br><br>",
-      "<strong>Comments per Newsgroup</strong><br>",
-      comments_per_newsgroup,
-      "</div>"  # End of custom tooltip styling
-    )
-  )
-
-# Identify current min and max sizes for nodes
-current_min <- min(nodes$size, na.rm = TRUE)
-current_max <- max(nodes$size, na.rm = TRUE)
-
-# Define new desired range for node sizes
-new_min <- 15  # Minimum size
-new_max <- 30  # Maximum size
-
-# Apply Min-Max scaling to the 'size' column
-nodes <- nodes %>%
-  mutate(
-    size = ((size - current_min) / (current_max - current_min)) * (new_max - new_min) + new_min
-  )
-
-nodes
-edges
-summary(nodes)
-summary(edges)
-```
-
-```{r Visualize the Graph}
-# Libraries
-library(dplyr)
-library(tidyr)
-library(visNetwork)
-library(igraph)  # Needed for community detection
-library(RColorBrewer)  # For generating pastel colors
-
-# Convert node names to zero-based indices
-nodes <- nodes %>%
-  mutate(id = 0:(n() - 1))  # Create a new 'id' column for nodes
-
-# Convert 'source' and 'target' in edges to indices using the 'name' to 'id' mapping
-edges <- edges %>%
-  mutate(
-    from = match(source, nodes$name) - 1,  # Zero-based index
-    to = match(target, nodes$name) - 1     # Zero-based index
-  )
-
-# Automatically assign colors to communities using RColorBrewer
-num_communities <- length(unique(node_communities$community))
-colors <- brewer.pal(min(num_communities, 9), "Set1")  # Use Set1 palette for distinct colors
-
-# If you have more than 9 communities and need more colors, you can create a larger palette
-# by repeating or expanding the Set1 palette
-if (num_communities > 9) {
-  colors <- colorRampPalette(brewer.pal(9, "Set1"))(num_communities)
-}
-# Merge nodes with their community data and assign colors automatically
-nodes <- nodes %>%
-  mutate(color = colors[community])
-
-# Create a network visualization with a force-directed layout
-network_graph <- visNetwork(nodes, edges, width = "100vw", height = "100vh") %>%
-  visNodes(
-    size = nodes$size * 5,
-    font = list(size = 15),
-    color = list(
-      border = "black",
-      highlight = "red"
-    ),
-    title = nodes$title  # Use the title for hover popups
-  ) %>%
-  visEdges(
-    width = ~weight,
-    color = list(color = 'gray', highlight = 'red'),
-    smooth = list(enabled = TRUE, type = "dynamic", roundness = 0.5)  # Enable smooth dynamic edges with medium roundness
-  ) %>%
-  visOptions(
-    highlightNearest = list(enabled = TRUE, hover = TRUE),
-    nodesIdSelection = list(enabled = TRUE)
-  ) %>%
-  visPhysics(
-    stabilization = TRUE,
-    solver = "barnesHut",
-    barnesHut = list(gravitationalConstant = -8000, springLength = 100, springConstant = 0.01)
-  ) %>%
-  visInteraction(
-    dragNodes = TRUE,
-    dragView = TRUE,
-    zoomView = TRUE
-  ) %>%
-  visLayout(
-    improvedLayout = TRUE
-  )
-
-# Display the network graph in the RStudio Viewer
-network_graph
-
-# Save the network graph to an HTML file with full width and height
-network_graph_path <- file.path(output_directory, "images and tables/network_graph.html")
-visSave(network_graph, file = network_graph_path)
-
-# Step 4: Add the custom legend directly into the HTML file after it is saved
-html_legend <- '
-<div style="position: absolute; bottom: 20px; right: 20px; background-color: white; border: 1px solid #666; padding: 10px; border-radius: 5px; font-family: Arial, sans-serif;">
-  <div style="margin-bottom: 5px;"><strong>Color</strong> = Community (Louvain)</div>
-  <div><strong>Node Size</strong> = Influence</div>
-</div>
-'
-
-# Inject the legend into the HTML file
-html_content <- readLines(network_graph_path)
-html_content <- c(html_content, html_legend)
-writeLines(html_content, network_graph_path)
-```
+# Author Impact Hypothesis

### 2024-09-01 Scripts - Data Cleaning and Visuals/_CSV Cleaning.Rmd
testing

@@
 
+Filtering to 1982-1986
+```{r Filtering to 1982-1986}
+all_comments <- all_comments %>%
+  filter(Date < as.Date("1987-01-01")) %>% filter(Date > as.Date("1982-01-01"))
+
+all_threads <- all_threads %>%
+  filter(Date < as.Date("1987-01-01")) %>% filter(Date > as.Date("1982-01-01"))
+
+write.csv(all_threads, file.path(threads_directory, "combined_threads_cleaned_82TO86.csv"), row.names = FALSE)
+write.csv(all_comments, file.path(comments_directory, "combined_comments_cleaned_82TO86.csv"), row.names = FALSE)
+```
+
 # Table and Figures
@@
 # Save the comments dataframe to CSV
-write.csv(comments_in_keyword_threads, file.path(comments_directory, "aids_related_comments.csv"), row.names = FALSE)
+write.csv(comments_in_keyword_threads, file.path(comments_directory, "aids_related_comments_82TO86.csv"), row.names = FALSE)
 
@@
 # Save the threads dataframe to CSV
-write.csv(threads_summary_df, file.path(threads_directory, "aids_related_threads.csv"), row.names = FALSE)
+write.csv(threads_summary_df, file.path(threads_directory, "aids_related_threads_82TO86.csv"), row.names = FALSE)
 ```

### 2024-09-01 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
saving work

@@
 # Theme Prevelance Hypothesis
+```{r}
+library(topicmodels)
+library(tm)
+library(SnowballC)
+library(tidytext)
+library(dplyr)
+library(ggplot2)
+library(igraph)
+library(ggraph)
+
+# Load the datasets
+all_comments <- read.csv("/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments/aids_related_comments_82TO86.csv")
+
+# Data preparation: Select relevant text data
+comments_corpus <- Corpus(VectorSource(all_comments$Content)) # Replace 'Content' with the actual column name containing text data
+
+# Text preprocessing
+comments_corpus <- comments_corpus %>%
+  tm_map(content_transformer(tolower)) %>%  # Convert text to lowercase
+  tm_map(removePunctuation) %>%              # Remove punctuation
+  tm_map(removeNumbers) %>%                  # Remove numbers
+  tm_map(removeWords, stopwords("english")) %>%  # Remove common stop words
+  tm_map(stemDocument) %>%                   # Perform stemming
+  tm_map(stripWhitespace)                    # Strip whitespace
+
+# Create Document-Term Matrix (DTM)
+dtm <- DocumentTermMatrix(comments_corpus)
+
+# Remove sparse terms to reduce the size of DTM
+dtm <- removeSparseTerms(dtm, 0.99) # Adjust sparsity threshold if necessary
+
+# Check for rows with all zero entries and remove them
+row_totals <- apply(dtm, 1, sum)
+dtm <- dtm[row_totals > 0, ]
+
+# Run LDA model to find themes (adjust number of topics as needed)
+set.seed(123) # Set seed for reproducibility
+lda_model <- LDA(dtm, k = 5, control = list(seed = 123)) # 'k' is the number of topics, adjust as needed
+
+# Display the top terms for each topic
+top_terms <- terms(lda_model, 10)
+print(top_terms)
+
+# Visualize the top terms for each topic (concise visualization)
+top_terms_df <- tidy(lda_model, matrix = "beta") %>%
+  group_by(topic) %>%
+  top_n(10, beta) %>%
+  ungroup() %>%
+  arrange(topic, -beta)
+
+# Plotting the top terms for each topic
+ggplot(top_terms_df, aes(reorder_within(term, beta, topic), beta, fill = factor(topic))) +
+  geom_col(show.legend = FALSE) +
+  facet_wrap(~ topic, scales = "free_y") +
+  coord_flip() +
+  scale_x_reordered() +
+  labs(title = "Top Terms in Each Topic", x = "Term", y = "Beta") +
+  theme_minimal()
+
+# Co-occurrence Network Analysis
+# Create a co-occurrence matrix
+term_matrix <- as.matrix(dtm)
+co_occurrence <- crossprod(term_matrix)
+
+# Build graph object
+graph <- graph_from_adjacency_matrix(co_occurrence, weighted = TRUE, mode = "undirected", diag = FALSE)
+V(graph)$name <- colnames(co_occurrence)
+
+# Simplify graph (remove loops and multiple edges)
+graph <- simplify(graph)
+
+# Visualize co-occurrence network
+set.seed(123)
+ggraph(graph, layout = 'fr') + 
+  geom_edge_link(aes(edge_alpha = weight), show.legend = FALSE) + 
+  geom_node_point(color = "blue", size = 5) + 
+  geom_node_text(aes(label = name), repel = TRUE) + 
+  theme_void() +
+  labs(title = "Co-occurrence Network of Themes")
+```
 

### 2024-09-01 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
adding visuals

--- 2024-09-01 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
@@
 # Theme Prevelance Hypothesis
+```{r Data Preparation}
+library(topicmodels)
+library(tm)
+library(SnowballC)
+library(tidytext)
+library(dplyr)
+library(ggplot2)
+library(igraph)
+library(ggraph)
+
+# Data preparation: Select relevant text data
+comments_corpus <- Corpus(VectorSource(all_comments$Full.Text)) # Replace 'Content' with the actual column name containing text data
+
+# Text preprocessing
+comments_corpus <- comments_corpus %>%
+  tm_map(content_transformer(tolower)) %>%  # Convert text to lowercase
+  tm_map(removePunctuation) %>%              # Remove punctuation
+  tm_map(removeNumbers) %>%                  # Remove numbers
+  tm_map(removeWords, stopwords("english")) %>%  # Remove common stop words
+  tm_map(stemDocument) %>%                   # Perform stemming
+  tm_map(stripWhitespace)                    # Strip whitespace
+
+# Create Document-Term Matrix (DTM)
+dtm <- DocumentTermMatrix(comments_corpus)
+
+# Remove sparse terms to reduce the size of DTM
+dtm <- removeSparseTerms(dtm, 0.92) # Adjust sparsity threshold if necessary
+
+# Check for rows with all zero entries and remove them
+row_totals <- apply(dtm, 1, sum)
+dtm <- dtm[row_totals > 0, ]
+```
+
+```{r How Many Topics}
+library(ldatuning)
+
+# Sample a smaller subset of the DTM
+set.seed(123)
+sample_indices <- sample(1:nrow(dtm), 1000)  # Reduce size to speed up
+sampled_dtm <- dtm[sample_indices, ]
+
+# Optimize LDA to find the best number of topics
+set.seed(123)
+result <- FindTopicsNumber(
+  sampled_dtm,
+  topics = seq(from = 2, to = 10, by = 1),  # Narrow topic range for faster computation
+  metrics = c("Griffiths2004", "Deveaud2014"),  # Use fewer metrics
+  method = "Gibbs",
+  control = list(seed = 123, iter = 500),  # Fewer iterations for quicker results
+  mc.cores = 6L,
+  verbose = TRUE
+)
+
+# Plot results to determine the optimal number of topics
+FindTopicsNumber_plot(result)
+```
+
+```{r LDA Model}
+# Run LDA model to find themes (adjust number of topics as needed)
+set.seed(123) # Set seed for reproducibility
+lda_model <- LDA(dtm, k = 5, control = list(seed = 123)) # 'k' is the number of topics, adjust as needed
+```
+
+```{Top Terms}
+# Display the top terms for each topic
+top_terms <- terms(lda_model, 10)
+print(top_terms)
+
+# Visualize the top terms for each topic (concise visualization)
+top_terms_df <- tidy(lda_model, matrix = "beta") %>%
+  group_by(topic) %>%
+  top_n(10, beta) %>%
+  ungroup() %>%
+  arrange(topic, -beta)
+
+# Plotting the top terms for each topic
+ggplot(top_terms_df, aes(reorder_within(term, beta, topic), beta, fill = factor(topic))) +
+  geom_col(show.legend = FALSE) +
+  facet_wrap(~ topic, scales = "free_y") +
+  coord_flip() +
+  scale_x_reordered() +
+  labs(title = "Top Terms in Each Topic", x = "Term", y = "Beta") +
+  theme_minimal()
+```
+
+```{r Co-occurrence Network Analysis}
+# Create a co-occurrence matrix
+term_matrix <- as.matrix(dtm)
+co_occurrence <- crossprod(term_matrix)
+
+# Build graph object
+graph <- graph_from_adjacency_matrix(co_occurrence, weighted = TRUE, mode = "undirected", diag = FALSE)
+V(graph)$name <- colnames(co_occurrence)
+
+# Simplify graph (remove loops and multiple edges)
+graph <- simplify(graph)
+
+# Visualize co-occurrence network
+set.seed(123)
+ggraph(graph, layout = 'fr') + 
+  geom_edge_link(aes(edge_alpha = weight), show.legend = FALSE) + 
+  geom_node_point(color = "blue", size = 5) + 
+  geom_node_text(aes(label = name), repel = TRUE) + 
+  theme_void() +
+  labs(title = "Co-occurrence Network of Themes")
+```
 

### 2024-09-01 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
new visuals

@@
 
-```{r How Many Topics}
+```{r How Many Topics, eval=FALSE, include=FALSE}
 library(ldatuning)
@@
 ```{r LDA Model}
-# Run LDA model to find themes (adjust number of topics as needed)
 set.seed(123) # Set seed for reproducibility
-lda_model <- LDA(dtm, k = 5, control = list(seed = 123)) # 'k' is the number of topics, adjust as needed
+lda_model <- LDA(dtm, k = 8, control = list(seed = 123)) # 'k' is the number of topics, adjust as needed
 ```

### 2024-09-01 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
made changes

@@
 # Load Directories
-output_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage"
+output_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage"
 threads_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads"
@@
 
+```{r Filtering For Relevancy}
+# Load necessary libraries
+library(ggplot2)
+library(dplyr)
+
+# Calculate the minimum and maximum of the 'Thread_Relevancy' column
+min_value <- min(all_threads$Thread_Relevancy, na.rm = TRUE)
+max_value <- max(all_threads$Thread_Relevancy, na.rm = TRUE)
+
+# Create four equal-sized bins between the min and max values
+breaks <- seq(min_value, max_value, length.out = 5)
+
+# Create a factor for quartile ranges based on these breaks
+all_threads$Quartile <- cut(
+  all_threads$Thread_Relevancy,
+  breaks = breaks,
+  labels = c("Q1", "Q2", "Q3", "Q4"),
+  include.lowest = TRUE
+)
+
+# Plot the bar graph showing the frequency of each quartile
+ggplot(all_threads, aes(x = Quartile)) +
+  geom_bar(fill = "skyblue", color = "black") +
+  geom_text(stat='count', aes(label=..count..), vjust=-0.5) +  # Add labels above bars
+  labs(title = "Frequency of Thread Relevancy Quartiles",
+       x = "Quartile",
+       y = "Frequency") +
+  theme_minimal()
+
+# Define the bin width manually
+bin_width <- 0.5
+
+# Plot the histogram with density overlay using all_threads
+ggplot(all_threads, aes(x = Thread_Relevancy)) +
+  geom_histogram(aes(y = ..count..), binwidth = bin_width, fill = "skyblue", color = "black", alpha = 0.7) + 
+  geom_density(aes(y = ..density.. * length(all_threads$Thread_Relevancy) * bin_width), fill = "orange", alpha = 0.4) +  # Scale density to match histogram counts
+  labs(title = "Histogram and Density of Thread Relevancy Scores",
+       x = "Relevancy",
+       y = "Number of Threads") +
+  theme_minimal()
+```
+
+```{r}
+# Filter out Quartile 1
+filtered_threads <- all_threads %>%
+  filter(Quartile != "Q1")
+
+# Plot the bar graph showing the frequency of each quartile
+ggplot(filtered_threads, aes(x = Quartile)) +
+  geom_bar(fill = "skyblue", color = "black") +
+  geom_text(stat='count', aes(label=..count..), vjust=-0.5) +  # Add labels above bars
+  labs(title = "Frequency of Thread Relevancy Quartiles",
+       x = "Quartile",
+       y = "Frequency") +
+  theme_minimal()
+
+# Define the bin width manually
+bin_width <- 0.5
+
+# Plot the histogram with density overlay using all_threads
+ggplot(filtered_threads, aes(x = Thread_Relevancy)) +
+  geom_histogram(aes(y = ..count..), binwidth = bin_width, fill = "skyblue", color = "black", alpha = 0.7) + 
+  geom_density(aes(y = ..density.. * bin_width * nrow(all_threads)), fill = "orange", alpha = 0.4) +  # Scale density to match histogram counts
+  labs(title = "Histogram and Density of Thread Relevancy Scores",
+       x = "Relevancy",
+       y = "Number of Threads") +
+  theme_minimal()
+```
+```{r Get Filtered Comments from Filtered Threads}
+# Filter threads with only one comment out of filtered threads 
+filtered_threads <- filtered_threads %>%
+  filter(Number.of.Messages > 1)
+
+# Filter the comments from 'all_comments' that match the filtered threads
+filtered_comments <- all_comments %>%
+  filter(Thread.ID %in% filtered_threads$Unique_ThreadID)
+
+# Check the result
+head(filtered_comments)
+```
+
+```{r Relevancy Filtered Descriptive Statistics}
+library(sjPlot)
+
+# Step 1: Group by newsgroup and calculate required statistics, including comment relevancy
+keywords_summary_df <- filtered_comments %>%
+  group_by(newsgroup) %>%
+  summarize(
+    Unique_Authors = n_distinct(Author),
+    Comments_with_Keywords = sum(Relevancy > 0),
+    Conversations_Mentioned_In = n_distinct(Thread.ID),
+    Total_Comments_In_Threads = n(),
+    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100,
+    Average_Relevancy_Score = mean(Relevancy, na.rm = TRUE)
+  )
+
+# Step 2: Calculate thread relevancy averages for filtered threads
+threads_summary_df_grouped <- filtered_threads %>%
+  group_by(newsgroup) %>%
+  summarize(Average_Thread_Relevancy = mean(Thread_Relevancy, na.rm = TRUE))
+
+# Step 3: Combine comment and thread summaries
+keywords_summary_df <- keywords_summary_df %>%
+  left_join(threads_summary_df_grouped, by = "newsgroup")
+
+total_unique_authors <- n_distinct(filtered_comments$Author)
+
+# Step 4: Add a totals row
+totals <- keywords_summary_df %>%
+  summarize(
+    newsgroup = "Total",
+    Comments_with_Keywords = sum(Comments_with_Keywords),
+    Conversations_Mentioned_In = sum(Conversations_Mentioned_In),
+    Total_Comments_In_Threads = sum(Total_Comments_In_Threads),
+    Unique_Authors = total_unique_authors,
+    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100,
+    Average_Relevancy_Score = mean(Average_Relevancy_Score, na.rm = TRUE),
+    Average_Thread_Relevancy = mean(Average_Thread_Relevancy, na.rm = TRUE)
+  )
+
+# Step 5: Combine the summary with the totals row
+keywords_summary_df <- bind_rows(keywords_summary_df, totals)
+
+# Correctly construct the output file path
+output_file_path <- file.path(output_directory, "images and tables", "aids_descriptive_statistics_table_relevancy_filtered.html")
+
+# Ensure the directory exists
+dir.create(dirname(output_file_path), recursive = TRUE, showWarnings = FALSE)
+
+# Use the constructed path for saving the file
+tab_df(keywords_summary_df, file = output_file_path)
+```
+
 # Theme Prevelance Hypothesis
@@
 # Remove sparse terms to reduce the size of DTM
-dtm <- removeSparseTerms(dtm, 0.92) # Adjust sparsity threshold if necessary
+dtm <- removeSparseTerms(dtm, 0.90) # Adjust sparsity threshold if necessary
 
@@
 
-```{Top Terms}
+```{r Top Terms}
 # Display the top terms for each topic
-top_terms <- terms(lda_model, 10)
+top_terms <- terms(lda_model, 20)
 print(top_terms)
@@
   group_by(topic) %>%
-  top_n(10, beta) %>%
+  top_n(20, beta) %>%
   ungroup() %>%
@@
 ```{r Co-occurrence Network Analysis}
-# Create a co-occurrence matrix
-term_matrix <- as.matrix(dtm)
-co_occurrence <- crossprod(term_matrix)
+# Step 1: Filter out terms with lower frequencies or less importance
+# You may set a threshold for filtering less relevant terms
+term_frequency <- rowSums(co_occurrence) # Calculate term frequency
+threshold <- quantile(term_frequency, 0.9) # Set threshold for top 10% most frequent terms
+filtered_terms <- which(term_frequency > threshold)
+filtered_co_occurrence <- co_occurrence[filtered_terms, filtered_terms]
 
-# Build graph object
-graph <- graph_from_adjacency_matrix(co_occurrence, weighted = TRUE, mode = "undirected", diag = FALSE)
-V(graph)$name <- colnames(co_occurrence)
+# Step 2: Create graph object with filtered terms
+graph <- graph_from_adjacency_matrix(filtered_co_occurrence, weighted = TRUE, mode = "undirected", diag = FALSE)
 
-# Simplify graph (remove loops and multiple edges)
+# Step 3: Simplify the graph to avoid self-loops and redundant edges
 graph <- simplify(graph)
 
-# Visualize co-occurrence network
-set.seed(123)
+# Step 4: Visualize the co-occurrence network with improved settings
+set.seed(123)  # For reproducibility
 ggraph(graph, layout = 'fr') + 
-  geom_edge_link(aes(edge_alpha = weight), show.legend = FALSE) + 
-  geom_node_point(color = "blue", size = 5) + 
-  geom_node_text(aes(label = name), repel = TRUE) + 
+  geom_edge_link(aes(edge_alpha = weight), show.legend = FALSE, edge_width = 0.2) + 
+  geom_node_point(color = "blue", size = 4) + 
+  geom_node_text(aes(label = name), repel = TRUE, max.overlaps = 20) + # Increase max.overlaps for ggrepel
   theme_void() +
-  labs(title = "Co-occurrence Network of Themes")
+  labs(title = "Co-occurrence Network of Key Themes")
 ```

### 2024-09-01 Scripts - Data Cleaning and Visuals/CSV Cleaning.Rmd
finished the first hyp code

--- 2024-09-01 Scripts - Data Cleaning and Visuals/_CSV Cleaning.Rmd
@@
 
+total_unique_authors <- n_distinct(comments_in_keyword_threads$Author)
+
 # Add a totals row
@@
     Total_Comments_In_Threads = sum(Total_Comments_In_Threads),
-    Unique_Authors = sum(Unique_Authors),
+    Unique_Authors = total_unique_authors,
     Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100,

### 2024-09-01 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
finished the first hyp code

@@
 library(RColorBrewer) 
+library(sjPlot)
+library(ldatuning)
+library(tm)
+library(SnowballC)
 
@@
 ```{r Filtering For Relevancy}
-# Load necessary libraries
-library(ggplot2)
-library(dplyr)
-
 # Calculate the minimum and maximum of the 'Thread_Relevancy' column
@@
 
-```{r}
-# Filter out Quartile 1
+```{r Filtering Out Quartile 1}
 filtered_threads <- all_threads %>%
@@
 ```{r Relevancy Filtered Descriptive Statistics}
-library(sjPlot)
-
 # Step 1: Group by newsgroup and calculate required statistics, including comment relevancy
@@
 ```{r Data Preparation}
-library(topicmodels)
-library(tm)
-library(SnowballC)
-library(tidytext)
-library(dplyr)
-library(ggplot2)
-library(igraph)
-library(ggraph)
-
 # Data preparation: Select relevant text data
-comments_corpus <- Corpus(VectorSource(all_comments$Full.Text)) # Replace 'Content' with the actual column name containing text data
+comments_corpus <- Corpus(VectorSource(filtered_comments$Full.Text)) # Replace 'Content' with the actual column name containing text data
 
@@
 ```{r How Many Topics, eval=FALSE, include=FALSE}
-library(ldatuning)
-
-# Sample a smaller subset of the DTM
-set.seed(123)
-sample_indices <- sample(1:nrow(dtm), 1000)  # Reduce size to speed up
-sampled_dtm <- dtm[sample_indices, ]
-
 # Optimize LDA to find the best number of topics
@@
 result <- FindTopicsNumber(
-  sampled_dtm,
+  dtm,
   topics = seq(from = 2, to = 10, by = 1),  # Narrow topic range for faster computation
@@
 set.seed(123) # Set seed for reproducibility
-lda_model <- LDA(dtm, k = 8, control = list(seed = 123)) # 'k' is the number of topics, adjust as needed
+lda_model <- LDA(dtm, k = 5, control = list(seed = 123)) # 'k' is the number of topics, adjust as needed
 ```
@@
 
-```{r Co-occurrence Network Analysis}
-# Step 1: Filter out terms with lower frequencies or less importance
-# You may set a threshold for filtering less relevant terms
+```{r Improved Co-occurrence Network Analysis}
+library(ggforce)
+library(ggrepel)
+library(ggplot2)
+library(igraph)
+
+# Step 1: Calculate Term Frequencies and Filter for Top Terms
+co_occurrence <- crossprod(as.matrix(dtm)) # Create co-occurrence matrix
+# Set a threshold to filter less relevant terms based on frequency
 term_frequency <- rowSums(co_occurrence) # Calculate term frequency
-threshold <- quantile(term_frequency, 0.9) # Set threshold for top 10% most frequent terms
+threshold <- quantile(term_frequency, 0.75) # Set threshold for top 25% most frequent terms
 filtered_terms <- which(term_frequency > threshold)
@@
 
-# Step 2: Create graph object with filtered terms
+# Step 2: Create a Graph Object with Filtered Terms
 graph <- graph_from_adjacency_matrix(filtered_co_occurrence, weighted = TRUE, mode = "undirected", diag = FALSE)
 
-# Step 3: Simplify the graph to avoid self-loops and redundant edges
+# Step 3: Simplify the Graph to Avoid Self-Loops and Redundant Edges
 graph <- simplify(graph)
 
-# Step 4: Visualize the co-occurrence network with improved settings
+# Step 4: Assign Topics to Terms Based on the LDA Model
+terms <- rownames(filtered_co_occurrence) # Extract terms from the filtered co-occurrence matrix
+term_topic_probs <- posterior(lda_model)$terms[, terms] # Extract term-topic probabilities for the filtered terms
+term_topic_assignment <- apply(term_topic_probs, 2, which.max) # Assign each term to the topic with the highest probability
+
+# Create a data frame mapping terms to topics
+term_topic_df <- data.frame(term = terms, topic = factor(term_topic_assignment))
+
+# Increase the repulsion and area in the layout algorithm
 set.seed(123)  # For reproducibility
-ggraph(graph, layout = 'fr') + 
-  geom_edge_link(aes(edge_alpha = weight), show.legend = FALSE, edge_width = 0.2) + 
-  geom_node_point(color = "blue", size = 4) + 
-  geom_node_text(aes(label = name), repel = TRUE, max.overlaps = 20) + # Increase max.overlaps for ggrepel
-  theme_void() +
-  labs(title = "Co-occurrence Network of Key Themes")
+graph_layout <- create_layout(graph, layout = layout_with_fr(graph, niter = 5000, area = vcount(graph)^3.5, repulserad = vcount(graph)^3.5))
+
+# Normalize the layout to ensure it fits within the plot
+graph_layout$x <- scale(graph_layout$x, center = TRUE, scale = TRUE) * 4  # Increase spread
+graph_layout$y <- scale(graph_layout$y, center = TRUE, scale = TRUE) * 4  # Increase spread
+
+# Create intuitive topic names based on LDA results
+topic_names <- c(
+  "Medical Testing & Treatment",
+  "Personal Experiences & Opinions",
+  "Disease Research & Transmission",
+  "Sexual Orientation & Behavior",
+  "Social Discussion & Impact"
+)
+term_topic_df$topic_name <- topic_names[term_topic_df$topic]
+
+# Create the improved plot with simplified legend
+co_occurrence_plot <- ggplot(graph_layout, aes(x = x, y = y)) +
+  geom_edge_link(aes(edge_alpha = weight), edge_width = 0.3, color = "gray70", alpha = 0.3) +
+  geom_node_point(aes(size = log1p(term_frequency[filtered_terms]), color = term_topic_df$topic_name), show.legend = TRUE, alpha = 0.8) +
+  geom_text_repel(aes(label = name), 
+                  max.overlaps = 20,
+                  force = 10,
+                  point.padding = 0.5,
+                  segment.color = "gray50",
+                  min.segment.length = 0,
+                  box.padding = 0.7,
+                  segment.size = 0.2,
+                  size = 8) +
+  geom_mark_hull(aes(group = term_topic_df$topic_name, fill = term_topic_df$topic_name), 
+                 alpha = 0.1, show.legend = FALSE) +
+  scale_size(range = c(2, 12), name = "Term Frequency") +
+  scale_color_brewer(palette = "Set1", name = "Topic") +
+  scale_fill_brewer(palette = "Set1", guide = "none") +  # Remove fill from legend
+  coord_cartesian(xlim = c(-7.5, 7.5), ylim = c(-7.5, 7.5)) +
+  theme_void(base_size = 16) +
+  theme(
+    aspect.ratio = 1,
+    legend.position = "right",
+    legend.box = "vertical",
+    plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),
+    plot.margin = margin(40, 40, 40, 40),
+    plot.background = element_rect(fill = "white", color = NA),
+    legend.text = element_text(size = 10),
+    legend.title = element_text(size = 12)
+  ) +
+  guides(color = guide_legend(override.aes = list(size = 5))) +
+  labs(title = "Co-occurrence Network of Key Themes in AIDS Discussion",
+       caption = "Node size represents term frequency. Colors indicate topics identified by LDA.")
+
+# Display the plot
+print(co_occurrence_plot)
+
+# Save the plot to a PNG file with increased size
+ggsave(file.path(output_directory, "images and tables", "co-occurrence_network.png"), 
+       plot = co_occurrence_plot, width = 20, height = 16, dpi = 300)  # Increased dimensions
 ```

### 2024-09-01 Scripts - Data Cleaning and Visuals/Webpage Visualizations.Rmd
finished the first hyp code

--- 2024-08-25 Scripts - Data Cleaning and Visuals/_Webpage Visualizations Code.Rmd
@@
 author: "Emerson Johnston"
-lastmodifeddate: "2024-08-24"
+lastmodifeddate: "2024-09-01"
 output:
@@
 # Load the datasets with the correct file paths
-all_threads = pd.read_csv(os.path.join(threads_directory, "threads_cleaned_82TO89.csv"))
-all_comments = pd.read_csv(os.path.join(comments_directory, "comments_cleaned_82TO89.csv"))
-```
-
-```{r R CSV Cleaning}
-all_threads <- all_threads %>% drop_na()
-all_comments <- all_comments %>% drop_na()
-
-# Ensure the 'Date' columns are properly formatted as Date objects
-all_comments$Date <- as.Date(all_comments$Date, format = "%Y-%m-%d")
-all_threads$Date <- as.Date(all_threads$Date, format = "%Y-%m-%d")
-
-# Filter the datasets to include only data before January 1, 1989
-all_comments <- all_comments %>%
-  filter(Date < as.Date("1989-01-01")) %>% filter(Date > as.Date("1982-01-01"))
-
-all_threads <- all_threads %>%
-  filter(Date < as.Date("1989-01-01")) %>% filter(Date > as.Date("1982-01-01"))
-
-write.csv(all_threads, file.path(threads_directory, "threads_cleaned_82TO89.csv"), row.names = FALSE)
-write.csv(all_comments, file.path(comments_directory, "comments_cleaned_82TO89.csv"), row.names = FALSE)
+all_threads = pd.read_csv(os.path.join(threads_directory, "aids_related_threads_82TO86.csv"))
+all_comments = pd.read_csv(os.path.join(comments_directory, "aids_related_comments_82TO86.csv"))
 ```

### 2024-09-01 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
did more'

@@
   tm_map(removeWords, stopwords("english")) %>%  # Remove common stop words
-  tm_map(stemDocument) %>%                   # Perform stemming
+#  tm_map(stemDocument) %>%                   # Perform stemming
   tm_map(stripWhitespace)                    # Strip whitespace
@@
   scale_fill_brewer(palette = "Set1", guide = "none") +  # Remove fill from legend
-  coord_cartesian(xlim = c(-7.5, 7.5), ylim = c(-7.5, 7.5)) +
+  coord_cartesian(xlim = c(-8, 8), ylim = c(-8, 8)) +
   theme_void(base_size = 16) +

### 2024-09-01 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
changing things

@@
 ```{r Top Terms}
-# Display the top terms for each topic
-top_terms <- terms(lda_model, 20)
-print(top_terms)
+# Load required libraries
+library(tidyr)
+library(dplyr)
+library(sjPlot)
 
-# Visualize the top terms for each topic (concise visualization)
-top_terms_df <- tidy(lda_model, matrix = "beta") %>%
+# Assuming top_terms_df is your data frame from the LDA analysis
+
+# Reshape the data frame to have each topic's terms and betas side by side
+reshaped_df <- top_terms_df %>%
   group_by(topic) %>%
-  top_n(20, beta) %>%
+  mutate(term_id = row_number()) %>%
   ungroup() %>%
-  arrange(topic, -beta)
+  pivot_wider(
+    names_from = topic,
+    values_from = c(term, beta),
+    names_glue = "Topic_{topic}_{.value}"
+  )
 
-# Plotting the top terms for each topic
-ggplot(top_terms_df, aes(reorder_within(term, beta, topic), beta, fill = factor(topic))) +
-  geom_col(show.legend = FALSE) +
-  facet_wrap(~ topic, scales = "free_y") +
-  coord_flip() +
-  scale_x_reordered() +
-  labs(title = "Top Terms in Each Topic", x = "Term", y = "Beta") +
-  theme_minimal()
+reshaped_df <- reshaped_df %>%
+  select(term_id, 
+         starts_with("Topic_1_term"), starts_with("Topic_1_beta"),
+         starts_with("Topic_2_term"), starts_with("Topic_2_beta"),
+         starts_with("Topic_3_term"), starts_with("Topic_3_beta"),
+         starts_with("Topic_4_term"), starts_with("Topic_4_beta"),
+         starts_with("Topic_5_term"), starts_with("Topic_5_beta"))
+
+# Create a styled table using sjPlot
+# tab_df(
+#  reshaped_df,
+#  title = "Top Terms and Betas for Each Topic",
+#  show.rownames = FALSE,
+#  digits = 2,
+#  file = output_file_path
+#  )
+
+library(dplyr)
+library(gt)
+
+# Create the gt table
+gt_table <- reshaped_df %>%
+  gt() %>%
+  tab_spanner(
+    label = "Topic 1",
+    columns = c("Topic_1_term", "Topic_1_beta")
+  ) %>%
+  tab_spanner(
+    label = "Topic 2",
+    columns = c("Topic_2_term", "Topic_2_beta")
+  ) %>%
+  tab_spanner(
+    label = "Topic 3",
+    columns = c("Topic_3_term", "Topic_3_beta")
+  ) %>%
+  tab_spanner(
+    label = "Topic 4",
+    columns = c("Topic_4_term", "Topic_4_beta")
+  ) %>%
+  tab_spanner(
+    label = "Topic 5",
+    columns = c("Topic_5_term", "Topic_5_beta")
+  ) %>%
+  cols_label(
+    term_id = "Term No.",
+    Topic_1_term = "term", Topic_1_beta = "beta",
+    Topic_2_term = "term", Topic_2_beta = "beta",
+    Topic_3_term = "term", Topic_3_beta = "beta",
+    Topic_4_term = "term", Topic_4_beta = "beta",
+    Topic_5_term = "term", Topic_5_beta = "beta"
+  )
+
+gt_table
+
+# Save the gt table to an HTML file
+output_file_path <- file.path(output_directory, "images and tables", "Top Terms and Betas for Each Topic.html")
+gtsave(gt_table, output_file_path)
 ```

### 2024-09-02 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
changes

@@
 
-```{python Python Load Libraries, Directories, and Datasets}
+```{python Python Load Libraries, Directories, and Datasets, eval=FALSE, include=FALSE}
 import os
@@
 )
+```
 
+```{r Plot How Many Topics}
 # Plot results to determine the optimal number of topics

### 2024-09-02 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
made modifications, finished hyp one

@@
 ```{r Data Preparation}
+# Load required libraries
+library(tm)
+
 # Data preparation: Select relevant text data
-comments_corpus <- Corpus(VectorSource(filtered_comments$Full.Text)) # Replace 'Content' with the actual column name containing text data
+comments_corpus <- Corpus(VectorSource(filtered_comments$Full.Text))  # Replace 'Full.Text' with the actual column name containing text data
 
@@
   tm_map(content_transformer(tolower)) %>%                   # Convert text to lowercase
+  tm_map(content_transformer(function(x) gsub("[^[:alnum:] ]", " ", x))) %>%  # Remove non-alphanumeric characters
   tm_map(removePunctuation) %>%                               # Remove punctuation
@@
   tm_map(removeWords, stopwords("english")) %>%               # Remove common stop words
-#  tm_map(stemDocument) %>%                   # Perform stemming
+  # tm_map(stemDocument) %>%                                  # Perform stemming (optional)
   tm_map(stripWhitespace)                                     # Strip whitespace
@@
   topics = seq(from = 2, to = 10, by = 1),  # Narrow topic range for faster computation
-  metrics = c("Griffiths2004", "Deveaud2014"),  # Use fewer metrics
+  metrics = c("Griffiths2004", "Deveaud2014", "CaoJuan2009", "Arun2010"),  # Use fewer metrics
   method = "Gibbs",
-  control = list(seed = 123, iter = 500),  # Fewer iterations for quicker results
-  mc.cores = 6L,
+  control = list(seed = 123, iter = 200),  # Fewer iterations for quicker results
+  mc.cores = 2L,
   verbose = TRUE
@@
 set.seed(123) # Set seed for reproducibility
-lda_model <- LDA(dtm, k = 5, control = list(seed = 123)) # 'k' is the number of topics, adjust as needed
+lda_model <- LDA(dtm, k = 6, control = list(seed = 123)) # 'k' is the number of topics, adjust as needed
 ```
@@
 
-# Assuming top_terms_df is your data frame from the LDA analysis
+# Visualize the top terms for each topic (concise visualization)
+top_terms_df <- tidy(lda_model, matrix = "beta") %>%
+  group_by(topic) %>%
+  top_n(20, beta) %>%
+  ungroup() %>%
+  arrange(topic, -beta)
+
+# Round beta values to 3 decimal places
+top_terms_df <- top_terms_df %>%
+  mutate(beta = round(beta, 3))
 
@@
          starts_with("Topic_4_term"), starts_with("Topic_4_beta"),
-         starts_with("Topic_5_term"), starts_with("Topic_5_beta"))
-
-# Create a styled table using sjPlot
-# tab_df(
-#  reshaped_df,
-#  title = "Top Terms and Betas for Each Topic",
-#  show.rownames = FALSE,
-#  digits = 2,
-#  file = output_file_path
-#  )
+         starts_with("Topic_5_term"), starts_with("Topic_5_beta"),
+         starts_with("Topic_6_term"), starts_with("Topic_6_beta"))
 
@@
   gt() %>%
-  tab_spanner(
-    label = "Topic 1",
-    columns = c("Topic_1_term", "Topic_1_beta")
-  ) %>%
-  tab_spanner(
-    label = "Topic 2",
-    columns = c("Topic_2_term", "Topic_2_beta")
-  ) %>%
-  tab_spanner(
-    label = "Topic 3",
-    columns = c("Topic_3_term", "Topic_3_beta")
-  ) %>%
-  tab_spanner(
-    label = "Topic 4",
-    columns = c("Topic_4_term", "Topic_4_beta")
-  ) %>%
-  tab_spanner(
-    label = "Topic 5",
-    columns = c("Topic_5_term", "Topic_5_beta")
-  ) %>%
+  tab_spanner(label = "Topic 1", columns = c("Topic_1_term", "Topic_1_beta")) %>%
+  tab_spanner(label = "Topic 2", columns = c("Topic_2_term", "Topic_2_beta")) %>%
+  tab_spanner(label = "Topic 3", columns = c("Topic_3_term", "Topic_3_beta")) %>%
+  tab_spanner(label = "Topic 4", columns = c("Topic_4_term", "Topic_4_beta")) %>%
+  tab_spanner(label = "Topic 5", columns = c("Topic_5_term", "Topic_5_beta")) %>%
+  tab_spanner(label = "Topic 6", columns = c("Topic_6_term", "Topic_6_beta")) %>%
   cols_label(
@@
     Topic_4_term = "term", Topic_4_beta = "beta",
-    Topic_5_term = "term", Topic_5_beta = "beta"
-  )
+    Topic_5_term = "term", Topic_5_beta = "beta", 
+    Topic_6_term = "term", Topic_6_beta = "beta")
 
@@
 topic_names <- c(
-  "Medical Testing & Treatment",
-  "Personal Experiences & Opinions",
-  "Disease Research & Transmission",
-  "Sexual Orientation & Behavior",
-  "Social Discussion & Impact"
+  "Topic 1",
+  "Topic 2",
+  "Topic 3",
+  "Topic 4",
+  "Topic 5",
+  "Topic 6"
 )

### 2024-09-02 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
did more

@@
 
-```{r Plot How Many Topics}
+```{r Plot How Many Topics, eval=FALSE, include=FALSE}
 # Plot results to determine the optimal number of topics
@@
 ```
+Six Topics!
 
@@
 
-```{r Improved Co-occurrence Network Analysis}
+```{r Co-occurrence Network Analysis}
 library(ggforce)
@@
 # Emotional Tone Hypothesis
+```{r Load All Datasets}
+usenet_comments_all <- read.csv(file.path(comments_directory, "combined_comments_cleaned_82TO86.csv"))
+usenet_threads_all  <- read.csv(file.path(threads_directory, "combined_threads_cleaned_82TO86.csv"))
+```
+
+```{r Descriptive Statistics Related to Sentiment}
+library(moments)
+
+# Calculate descriptive statistics for AIDS-related discussions
+aids_sentiment_stats <- filtered_comments %>%
+  summarize(
+    Min = min(SentimentScore, na.rm = TRUE),
+    Max = max(SentimentScore, na.rm = TRUE),
+    Range = max(SentimentScore, na.rm = TRUE) - min(SentimentScore, na.rm = TRUE),
+    Mean = mean(SentimentScore, na.rm = TRUE),
+    Median = median(SentimentScore, na.rm = TRUE),
+    SD = sd(SentimentScore, na.rm = TRUE),
+    Skewness = skewness(SentimentScore, na.rm = TRUE),
+    Kurtosis = kurtosis(SentimentScore, na.rm = TRUE)
+  ) %>%
+  mutate(Dataset = "Dataset Three")
+
+# Calculate descriptive statistics for the entire Usenet dataset
+usenet_sentiment_stats <- usenet_comments_all %>%
+  summarize(
+    Min = min(SentimentScore, na.rm = TRUE),
+    Max = max(SentimentScore, na.rm = TRUE),
+    Range = max(SentimentScore, na.rm = TRUE) - min(SentimentScore, na.rm = TRUE),
+    Mean = mean(SentimentScore, na.rm = TRUE),
+    Median = median(SentimentScore, na.rm = TRUE),
+    SD = sd(SentimentScore, na.rm = TRUE),
+    Skewness = skewness(SentimentScore, na.rm = TRUE),
+    Kurtosis = kurtosis(SentimentScore, na.rm = TRUE)
+  ) %>%
+  mutate(Dataset = "Dataset One")
+
+# Combine the descriptive statistics into one table
+combined_sentiment_stats <- bind_rows(aids_sentiment_stats, usenet_sentiment_stats) %>%
+  select(Dataset, everything())  # Ensure 'Dataset' column is the first column
+
+combined_sentiment_stats
+```
+
+```{r Identify Influential Authors by Number of Connections}
+# Load necessary libraries
+library(dplyr)
+library(igraph)
+
+# Step 1: Create an edge list based on co-participation in threads
+edges <- filtered_comments %>%
+  filter(Thread.ID != "") %>%  # Ensure Thread.ID is not empty
+  group_by(Thread.ID) %>%
+  filter(n() > 1) %>%  # Only consider threads with more than one comment
+  summarize(edgelist = list(combn(Author, 2, simplify = FALSE))) %>%  # Create pairwise combinations of authors
+  unnest(edgelist) %>%
+  unnest_wider(edgelist, names_sep = "") %>%
+  rename(source = edgelist1, target = edgelist2) %>%
+  filter(source != target) %>%  # Remove self-loops
+  group_by(source, target) %>%
+  summarize(weight = n(), .groups = 'drop')  # Count the number of co-participations as edge weight
+
+# Step 2: Create a graph object from the edge list
+graph <- igraph::graph_from_data_frame(edges, directed = FALSE)
+
+# Step 3: Calculate the degree (number of connections) for each author
+author_influence <- data.frame(
+  Author = igraph::V(graph)$name,
+  Influence = igraph::degree(graph)
+)
+
+# Step 4: Identify the top 15 most influential authors
+top_influential_authors <- author_influence %>%
+  arrange(desc(Influence)) %>%  # Sort authors by descending influence
+  slice(1:15)  # Select the top 15 authors
+
+# Display the list of top 15 influential authors
+print(top_influential_authors)
+```
+
+```{r Calculate and Print Author Influence on Sentiment Scores}
+# Filter the all_comments dataset to only include posts by the top 15 influential authors
+top_authors_comments <- filtered_comments %>%
+  filter(Author %in% top_influential_authors$Author)
+
+# Calculate descriptive statistics for the sentiment scores of influential authors
+influential_authors_sentiment_stats <- top_authors_comments %>%
+  summarize(
+    Min = min(SentimentScore, na.rm = TRUE),
+    Max = max(SentimentScore, na.rm = TRUE),
+    Range = max(SentimentScore, na.rm = TRUE) - min(SentimentScore, na.rm = TRUE),
+    Mean = mean(SentimentScore, na.rm = TRUE),
+    Median = median(SentimentScore, na.rm = TRUE),
+    SD = sd(SentimentScore, na.rm = TRUE),
+    Skewness = skewness(SentimentScore, na.rm = TRUE),
+    Kurtosis = kurtosis(SentimentScore, na.rm = TRUE)
+  ) %>%
+  mutate(Dataset = "Influential Authors")
+
+# Combine the sentiment statistics into one table
+combined_sentiment_stats <- bind_rows(
+  aids_sentiment_stats,  # AIDS-related discussions
+  usenet_sentiment_stats,  # Entire Usenet dataset
+  influential_authors_sentiment_stats  # Influential authors
+) %>%
+  select(Dataset, everything())  # Ensure 'Dataset' column is the first column
+
+# Correctly construct the output file path
+output_file_path <- file.path(output_directory, "images and tables", "sentiment_score_descriptive_statistics_combined.html")
+
+combined_sentiment_stats
+
+# Display the combined descriptive statistics table using sjPlot
+tab_df(
+  combined_sentiment_stats,
+  title = "Descriptive Statistics for Sentiment Scores of Different Datasets",
+  show.rownames = FALSE,
+  show.ci = FALSE,
+  show.p = FALSE,
+  digits = 2,
+  file = output_file_path)
+```
+
+```{r Time Series Plot of Sentiment Scores}
+# Ensure necessary libraries are loaded
+library(ggplot2)
+library(dplyr)
+
+# Convert Date columns to Date type
+filtered_comments$Date <- as.Date(filtered_comments$Date)
+usenet_comments_all$Date <- as.Date(usenet_comments_all$Date)
+
+# Calculate monthly average sentiment scores for AIDS-related discussions
+monthly_sentiment_aids <- filtered_comments %>%
+  group_by(Month = as.Date(format(Date, "%Y-%m-01"))) %>%
+  summarize(AverageSentiment = mean(SentimentScore, na.rm = TRUE))
+
+# Calculate monthly average sentiment scores for the entire Usenet dataset
+monthly_sentiment_usenet <- usenet_comments_all %>%
+  group_by(Month = as.Date(format(Date, "%Y-%m-01"))) %>%
+  summarize(AverageSentiment = mean(SentimentScore, na.rm = TRUE))
+
+# Filter the all_comments dataset to only include posts by the top 15 influential authors
+top_authors_comments <- filtered_comments %>%
+  filter(Author %in% top_influential_authors$Author)
+
+# Calculate monthly average sentiment scores for the influential authors
+monthly_sentiment_influential <- top_authors_comments %>%
+  group_by(Month = as.Date(format(Date, "%Y-%m-01"))) %>%
+  summarize(AverageSentiment = mean(SentimentScore, na.rm = TRUE))
+
+# Combine the datasets for plotting
+combined_monthly_sentiment <- bind_rows(
+  monthly_sentiment_usenet %>% mutate(Dataset = "Dataset One"),
+  monthly_sentiment_aids %>% mutate(Dataset = "Dataset Three"),
+  monthly_sentiment_influential %>% mutate(Dataset = "Influential Authors")
+)
+
+# Create the time series plot with a white background and no legend title
+time_series_plot <- ggplot(combined_monthly_sentiment, aes(x = Month, y = AverageSentiment, color = Dataset)) +
+  geom_line(size = 1.2) +
+  labs(
+    title = "Time Series of Average Sentiment Scores Over Time",
+    x = "Month",
+    y = "Average Sentiment Score"
+  ) +
+  theme_bw() +  # Use theme_bw() for a white background
+  theme(legend.position = "bottom") +
+  guides(color = guide_legend(title = NULL))  # Remove the legend title
+
+# Print the plot to the R console
+print(time_series_plot)
+
+# Save the plot to a PNG file
+output_file_path <- file.path(output_directory, "images and tables", "time_series_sentiment_plot.png")
+ggsave(output_file_path, plot = time_series_plot, width = 10, height = 6, dpi = 300)
+```
 
 # Author Impact Hypothesis
+```{r LDA Model for Influential Authors}
+# Prepare the corpus for influential authors
+influential_corpus <- Corpus(VectorSource(top_authors_comments$Full.Text))
+influential_corpus <- tm_map(influential_corpus, content_transformer(tolower))
+influential_corpus <- tm_map(influential_corpus, removePunctuation)
+influential_corpus <- tm_map(influential_corpus, removeNumbers)
+influential_corpus <- tm_map(influential_corpus, removeWords, stopwords("english"))
+influential_corpus <- tm_map(influential_corpus, stripWhitespace)
+
+# Create DTM for influential authors
+influential_dtm <- DocumentTermMatrix(influential_corpus)
+influential_dtm <- removeSparseTerms(influential_dtm, 0.90)
+```
+
+```{r How Many Topics}
+# Optimize LDA to find the best number of topics
+set.seed(123)
+result <- FindTopicsNumber(
+  influential_dtm,
+  topics = seq(from = 2, to = 10, by = 1),  # Narrow topic range for faster computation
+  metrics = c("Griffiths2004", "Deveaud2014", "CaoJuan2009", "Arun2010"),  # Use fewer metrics
+  method = "Gibbs",
+  control = list(seed = 123, iter = 200),  # Fewer iterations for quicker results
+  mc.cores = 2L,
+  verbose = TRUE
+)
+
+# Plot results to determine the optimal number of topics
+FindTopicsNumber_plot(result)
+```
+
+```{r LDA Model and Top Terms}
+# LDA for influential authors
+set.seed(123)
+influential_lda <- LDA(influential_dtm, k = 6, control = list(seed = 123))
+
+# Load required libraries
+library(tidyr)
+library(dplyr)
+library(sjPlot)
+
+# Visualize the top terms for each topic (concise visualization)
+influential_topics <- tidy(influential_lda, matrix = "beta") %>%
+  group_by(topic) %>%
+  top_n(20, beta) %>%
+  ungroup() %>%
+  arrange(topic, -beta)
+
+# Round beta values to 3 decimal places
+influential_topics <- influential_topics %>%
+  mutate(beta = round(beta, 3))
+
+# Reshape the data frame to have each topic's terms and betas side by side
+reshaped_df <- influential_topics %>%
+  group_by(topic) %>%
+  mutate(term_id = row_number()) %>%
+  ungroup() %>%
+  pivot_wider(
+    names_from = topic,
+    values_from = c(term, beta),
+    names_glue = "Topic_{topic}_{.value}"
+  )
+
+reshaped_df <- reshaped_df %>%
+  select(term_id, 
+         starts_with("Topic_1_term"), starts_with("Topic_1_beta"),
+         starts_with("Topic_2_term"), starts_with("Topic_2_beta"),
+         starts_with("Topic_3_term"), starts_with("Topic_3_beta"),
+         starts_with("Topic_4_term"), starts_with("Topic_4_beta"),
+         starts_with("Topic_5_term"), starts_with("Topic_5_beta"),
+         starts_with("Topic_6_term"), starts_with("Topic_6_beta"))
+
+library(dplyr)
+library(gt)
+
+# Create the gt table
+gt_table <- reshaped_df %>%
+  gt() %>%
+  tab_spanner(label = "Topic 1", columns = c("Topic_1_term", "Topic_1_beta")) %>%
+  tab_spanner(label = "Topic 2", columns = c("Topic_2_term", "Topic_2_beta")) %>%
+  tab_spanner(label = "Topic 3", columns = c("Topic_3_term", "Topic_3_beta")) %>%
+  tab_spanner(label = "Topic 4", columns = c("Topic_4_term", "Topic_4_beta")) %>%
+  tab_spanner(label = "Topic 5", columns = c("Topic_5_term", "Topic_5_beta")) %>%
+  tab_spanner(label = "Topic 6", columns = c("Topic_6_term", "Topic_6_beta")) %>%
+  cols_label(
+    term_id = "Term No.",
+    Topic_1_term = "term", Topic_1_beta = "beta", 
+    Topic_2_term = "term", Topic_2_beta = "beta",
+    Topic_3_term = "term", Topic_3_beta = "beta", 
+    Topic_4_term = "term", Topic_4_beta = "beta",
+    Topic_5_term = "term", Topic_5_beta = "beta", 
+    Topic_6_term = "term", Topic_6_beta = "beta")
+
+gt_table
+
+# Save the gt table to an HTML file
+output_file_path <- file.path(output_directory, "images and tables", "Top Terms and Betas for Each Topic (Influential Authors).html")
+gtsave(gt_table, output_file_path)
+```
+
+```{r Topic Matching}
+# Extract top terms from the overall LDA model (assuming it's stored in 'lda_model')
+overall_topics <- tidy(lda_model, matrix = "beta") %>%
+  group_by(topic) %>%
+  top_n(20, beta) %>%
+  ungroup() %>%
+  arrange(topic, -beta)
+
+# Function to calculate Jaccard similarity
+jaccard_similarity <- function(set1, set2) {
+  intersection <- length(intersect(set1, set2))
+  union <- length(union(set1, set2))
+  return(intersection / union)
+}
+
+# Compare topics
+topic_similarities <- data.frame(
+  Influential_Topic = numeric(),
+  Overall_Topic = numeric(),
+  Similarity = numeric()
+)
+
+for (i in 1:6) {
+  influential_terms <- influential_topics %>% filter(topic == i) %>% pull(term)
+  for (j in 1:6) {
+    overall_terms <- overall_topics %>% filter(topic == j) %>% pull(term)
+    similarity <- jaccard_similarity(influential_terms, overall_terms)
+    topic_similarities <- rbind(topic_similarities, data.frame(
+      Influential_Topic = i,
+      Overall_Topic = j,
+      Similarity = similarity
+    ))
+  }
+}
+
+# Find the best matching topics
+best_matches <- topic_similarities %>%
+  group_by(Influential_Topic) %>%
+  slice_max(order_by = Similarity, n = 1)
+
+tab_df(best_matches)
+```
+
+```{r Similarity Plot}
+library(ggplot2)
+
+ggplot(best_matches, aes(x = factor(Influential_Topic), y = Similarity, fill = factor(Overall_Topic))) +
+  geom_bar(stat = "identity") +
+  labs(title = "Similarity Between Influential Authors' Topics and Overall Topics",
+       x = "Influential Authors' Topic",
+       y = "Jaccard Similarity",
+       fill = "Best Matching Overall Topic") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+ggsave(file.path(output_directory, "images and tables", "topic_influence_comparison.png"), 
+       width = 10, height = 6, dpi = 300)
+```

### 2024-09-02 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
made important changes

@@
 print(top_influential_authors)
+
+output_file_path <- file.path(output_directory, "images and tables", "influential_authors_descriptive_statistics.html")
+
+tab_df(top_influential_authors,
+  file = output_file_path)
 ```
@@
 
+# Add key event annotations
+key_events <- data.frame(
+  date = as.Date(c("1982-05-11", "1983-09-30", "1984-04-23", "1984-10-01", 
+                   "1985-03-02", "1985-07-25", "1985-10-02", "1986-02-01", 
+                   "1986-08-14")),  # Add the key event dates
+  event = c("Term 'AIDS' Introduced", "CDC AIDS Guidelines", "HHS HIV/AIDS", 
+            "First HIV Blood Test", "First HIV Test Approved", "Rock Hudson's Diagnosis", 
+            "HIV Transmission Routes", "'HIV' Renamed", "AZT Approved"),  # Shorter descriptions
+  y = c(-25, -25, -25, -25, -25, -25, -25, -25, -25)  # Set y position for text labels
+)
+
+# Adding the annotations to the plot
+time_series_plot <- time_series_plot +
+  geom_vline(data = key_events, aes(xintercept = date), linetype = "dashed", alpha = 0.5) +  # Vertical dashed lines
+  geom_text(data = key_events, aes(x = date, y = y, label = event), 
+            size = 3, angle = 90, vjust = -0.5, hjust = 0, inherit.aes = FALSE)  # Event labels
+
 # Print the plot to the R console
@@
 
-```{r How Many Topics}
+```{r How Many Topics, eval=FALSE, include=FALSE}
 # Optimize LDA to find the best number of topics
@@
 ```
+
+Six Topics!
 
@@
 
-tab_df(best_matches)
+output_file_path <- file.path(output_directory, "images and tables", "topic_matches_table.html")
+
+tab_df(best_matches, ,
+  file = output_file_path)
 ```
@@
 ```
+
+```{r Topic Prevelance over Time Plot}
+library(tidyverse)
+library(lubridate)
+library(ggplot2)
+library(scales)
+library(topicmodels)
+
+# Function to get topic distributions for a set of documents
+get_topic_distribution <- function(lda_model, dtm) {
+  topic_dist <- posterior(lda_model)$topics
+  colnames(topic_dist) <- paste0("Topic_", 1:ncol(topic_dist))
+  cbind(data.frame(Document = rownames(dtm)), as.data.frame(topic_dist))
+}
+
+# Get topic distributions for all documents and influential authors' documents
+all_topic_dist <- get_topic_distribution(lda_model, dtm)
+influential_topic_dist <- get_topic_distribution(influential_lda, influential_dtm)
+
+# Add date and author information
+all_topic_dist$Date <- filtered_comments$Date[match(all_topic_dist$Document, rownames(dtm))]
+all_topic_dist$Influential <- FALSE
+
+influential_topic_dist$Date <- top_authors_comments$Date[match(influential_topic_dist$Document, rownames(influential_dtm))]
+influential_topic_dist$Influential <- TRUE
+
+# Combine datasets
+combined_topic_dist <- rbind(all_topic_dist, influential_topic_dist)
+
+# Calculate monthly topic prevalence
+monthly_topic_prevalence <- combined_topic_dist %>%
+  mutate(Month = floor_date(Date, "month")) %>%
+  group_by(Month, Influential) %>%
+  summarise(across(starts_with("Topic_"), mean)) %>%
+  pivot_longer(cols = starts_with("Topic_"), names_to = "Topic", values_to = "Prevalence")
+
+# Create a custom labeler for facet labels
+facet_labels <- c(`FALSE` = "All Authors", `TRUE` = "Influential Authors")
+
+# Create the line plot for topic prevalence over time with better scaling
+line_plot <- ggplot(monthly_topic_prevalence, aes(x = Month, y = Prevalence, color = Topic, group = Topic)) +
+  geom_line(size = 1.5) +  # Increase line size for better visibility
+  facet_wrap(~Influential, scales = "free_y", ncol = 1, labeller = labeller(Influential = facet_labels)) +  # Use labeller to rename facets
+  scale_color_brewer(palette = "Dark2") +  # Use a palette with more distinct colors
+  labs(title = "Topic Prevalence Over Time: Influential Authors vs Overall Discussion",
+       x = "Date",
+       y = "Topic Prevalence",
+       color = "Topic") +
+  theme_bw() +
+  theme(legend.position = "bottom",
+        axis.text.x = element_text(angle = 45, hjust = 1)) +  # Rotate x-axis labels for better readability
+  scale_x_date(date_breaks = "6 months", date_labels = "%b %Y") +
+  scale_y_continuous(labels = scales::percent_format(), limits = c(0.155, 0.1825))  # Zoom in on relevant y-axis range
+
+# Print the plot
+print(line_plot)
+
+# Save the plot with a higher DPI for better clarity
+output_file_path <- file.path(output_directory, "images and tables", "topic_prevalence_line_plot.png")
+ggsave(output_file_path, plot = line_plot, width = 12, height = 8, dpi = 300)
+```

### 2024-09-02 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
new tables and reorg

@@
 # Correctly construct the output file path
-output_file_path <- file.path(output_directory, "images and tables", "aids_descriptive_statistics_table_relevancy_filtered.html")
+output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_aids_relevancy_filtered.html")
 
@@
 # Save the gt table to an HTML file
-output_file_path <- file.path(output_directory, "images and tables", "Top Terms and Betas for Each Topic.html")
+output_file_path <- file.path(output_directory, "images and tables", "table_top_terms_and_betas_(all_authors).html")
 gtsave(gt_table, output_file_path)
@@
 # Save the plot to a PNG file with increased size
-ggsave(file.path(output_directory, "images and tables", "co-occurrence_network.png"), 
+ggsave(file.path(output_directory, "images and tables", "plot_co-occurrence_network.png"), 
        plot = co_occurrence_plot, width = 20, height = 16, dpi = 300)  # Increased dimensions
@@
 
-output_file_path <- file.path(output_directory, "images and tables", "influential_authors_descriptive_statistics.html")
+output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_influential_authors.html")
 
@@
 combined_sentiment_stats <- bind_rows(
+  usenet_sentiment_stats,  # Entire Usenet dataset
   aids_sentiment_stats,  # AIDS-related discussions
-  usenet_sentiment_stats,  # Entire Usenet dataset
   influential_authors_sentiment_stats  # Influential authors
@@
 # Correctly construct the output file path
-output_file_path <- file.path(output_directory, "images and tables", "sentiment_score_descriptive_statistics_combined.html")
+output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_sentiment_scores_combined.html")
 
@@
 # Save the plot to a PNG file
-output_file_path <- file.path(output_directory, "images and tables", "time_series_sentiment_plot.png")
+output_file_path <- file.path(output_directory, "images and tables", "plot_time_series_sentiment_line_graph.png")
 ggsave(output_file_path, plot = time_series_plot, width = 10, height = 6, dpi = 300)
@@
 # Save the gt table to an HTML file
-output_file_path <- file.path(output_directory, "images and tables", "Top Terms and Betas for Each Topic (Influential Authors).html")
+output_file_path <- file.path(output_directory, "images and tables", "table_top_terms_and_betas_(influential_authors).html")
 gtsave(gt_table, output_file_path)
@@
 
-output_file_path <- file.path(output_directory, "images and tables", "topic_matches_table.html")
+output_file_path <- file.path(output_directory, "images and tables", "table_topic_matches.html")
 
@@
 
-ggsave(file.path(output_directory, "images and tables", "topic_influence_comparison.png"), 
+ggsave(file.path(output_directory, "images and tables", "plot_topic_influence_comparison_bar_graph.png"), 
        width = 10, height = 6, dpi = 300)
@@
 # Save the plot with a higher DPI for better clarity
-output_file_path <- file.path(output_directory, "images and tables", "topic_prevalence_line_plot.png")
+output_file_path <- file.path(output_directory, "images and tables", "plot_topic_prevalence_line_graph.png")
 ggsave(output_file_path, plot = line_plot, width = 12, height = 8, dpi = 300)

### 2024-09-02 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
finished preliminary code

@@
        y = "Frequency") +
-  theme_minimal()
+  theme_bw()
 
@@
        y = "Number of Threads") +
-  theme_minimal()
+  theme_bw()
 ```
@@
 
-output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_influential_authors.html")
-
-tab_df(top_influential_authors,
-  file = output_file_path)
-```
-
-```{r Calculate and Print Author Influence on Sentiment Scores}
 # Filter the all_comments dataset to only include posts by the top 15 influential authors
@@
 
+# Assuming `top_authors_comments` already filters the dataset for top influential authors
+top_authors_comments_summary <- top_authors_comments %>%
+  group_by(Author) %>%
+  summarize(
+    Num_Comments = n(),  # Number of comments
+    Num_Threads = n_distinct(Thread.ID),  # Number of unique threads
+    Threads_Started = sum(Thread_Relative_CommentID == "CM00004", na.rm = TRUE),  # Number of threads started
+    Avg_Sentiment = mean(SentimentScore, na.rm = TRUE),  # Average sentiment score
+    Avg_Relevancy = mean(Relevancy, na.rm = TRUE)  # Average relevancy score
+  )
+
+# Merge this summary with the original `top_influential_authors` dataframe if needed
+influential_authors_metadata <- top_influential_authors %>%
+  left_join(top_authors_comments_summary, by = "Author")
+
+# Calculate totals for each numeric column
+totals_row <- influential_authors_metadata %>%
+  summarize(
+    Author = "Total",
+    Influence = sum(Influence, na.rm = TRUE),
+    Num_Comments = sum(Num_Comments, na.rm = TRUE),
+    Num_Threads = sum(Num_Threads, na.rm = TRUE),
+    Threads_Started = sum(Threads_Started, na.rm = TRUE),
+    Avg_Sentiment = mean(Avg_Sentiment, na.rm = TRUE),  # This is an average; sum might not make sense for sentiment
+    Avg_Relevancy = mean(Avg_Relevancy, na.rm = TRUE)   # This is an average; sum might not make sense for relevancy
+  )
+
+# Bind the totals row to the bottom of the dataframe
+influential_authors_metadata_with_totals <- bind_rows(influential_authors_metadata, totals_row)
+
+# Display the updated table with totals
+print(influential_authors_metadata_with_totals)
+
+output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_influential_authors.html")
+tab_df(influential_authors_metadata_with_totals, file = output_file_path)
+```
+
+```{r Calculate and Print Author Influence on Sentiment Scores}
 # Calculate descriptive statistics for the sentiment scores of influential authors
@@
   ) %>%
-  mutate(Dataset = "Influential Authors")
+  mutate(Dataset = "Dataset Four")
 
@@
 
+print(best_matches)
+
 output_file_path <- file.path(output_directory, "images and tables", "table_topic_matches.html")
@@
   file = output_file_path)
+
+# Transpose the 'best_matches' dataframe
+transposed_best_matches <- as.data.frame(t(best_matches))
+
+# Display the transposed table
+print(transposed_best_matches)
+
+output_file_path_transposed <- file.path(output_directory, "images and tables", "table_topic_matches_transposed.html")
+tab_df(transposed_best_matches,
+  file = output_file_path_transposed)
 ```
@@
 
-ggplot(best_matches, aes(x = factor(Influential_Topic), y = Similarity, fill = factor(Overall_Topic))) +
+# Create the bar chart and annotate with similarity values
+similarity_plot <- ggplot(best_matches, aes(x = factor(Influential_Topic), y = Similarity, fill = factor(Overall_Topic))) +
   geom_bar(stat = "identity") +
+  geom_text(aes(label = round(Similarity, 2)), 
+            position = position_stack(vjust = 0.5), size = 3) + # Add similarity score annotations
   labs(title = "Similarity Between Influential Authors' Topics and Overall Topics",
@@
        fill = "Best Matching Overall Topic") +
-  theme_minimal() +
+  theme_bw() +
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+similarity_plot
 
@@
 ```
+
+```{r Distribution of Comments per Newsgroup Plot}
+# Load necessary libraries
+library(ggplot2)
+library(dplyr)
+
+# Calculate the total number of comments per author across all newsgroups
+total_comments_by_author <- filtered_comments %>%
+  group_by(Author) %>%
+  summarise(Total_Comments = n())
+
+# Calculate the number of comments per author per newsgroup
+top_authors_by_newsgroup <- filtered_comments %>%
+  group_by(Author, newsgroup) %>%
+  summarise(Number_of_Comments = n())
+
+# Join the total comments data to the newsgroup data
+top_authors_by_newsgroup <- top_authors_by_newsgroup %>%
+  left_join(total_comments_by_author, by = "Author")
+
+# Select the top 15 most active authors by total number of comments
+top_15_authors <- total_comments_by_author %>%
+  arrange(desc(Total_Comments)) %>%
+  slice(1:15)  # Ensure only the top 25 authors are selected
+
+# Filter the main data to include only the top 25 authors
+top_15_data <- top_authors_by_newsgroup %>%
+  filter(Author %in% top_15_authors$Author)
+
+# Create the bar plot using ggplot2 and sort authors in descending order by total number of comments
+bar_plot <- ggplot(top_15_data, aes(x = Number_of_Comments, y = reorder(Author, Total_Comments), fill = newsgroup)) +
+  geom_bar(stat = "identity") +
+  labs(title = "Top 15 Most Active Users in Dataset Three by Newsgroup",
+       x = "Number of Comments",
+       y = "Author",
+       fill = "Newsgroup") +
+  theme_bw() +
+  theme(legend.position = "right",
+        axis.text.x = element_text(angle = 45, hjust = 1))
+
+# Print the plot
+print(bar_plot)
+
+# Save the plot to a file
+output_file_path <- file.path(output_directory, "images and tables/plot_top_15_most_active_users_by_newsgroup.png")
+ggsave(output_file_path, plot = bar_plot, width = 10, height = 6, dpi = 300)
+```
+```{r Thematic evolution}
+library(tidytext)
+library(tidyverse)
+
+# Identify top keywords for influential authors
+influential_keywords <- top_authors_comments %>%
+  unnest_tokens(word, Full.Text) %>%
+  anti_join(stop_words) %>%
+  count(Author, word, sort = TRUE) %>%
+  group_by(Author) %>%
+  top_n(5, n) %>%
+  ungroup()
+
+# Get the top 20 keywords across all influential authors
+top_keywords <- influential_keywords %>%
+  group_by(word) %>%
+  summarise(total = sum(n)) %>%
+  top_n(20, total) %>%
+  pull(word)
+
+# Function to calculate keyword prevalence
+calculate_keyword_prevalence <- function(df, keywords) {
+  df %>%
+    unnest_tokens(word, Full.Text) %>%
+    filter(word %in% keywords) %>%
+    count(Date = floor_date(Date, "month"), word) %>%
+    complete(Date, word, fill = list(n = 0)) %>%
+    group_by(Date) %>%
+    mutate(prevalence = n / sum(n)) %>%
+    ungroup()
+}
+
+# Calculate keyword prevalence for influential authors and overall discussions
+influential_prevalence <- calculate_keyword_prevalence(top_authors_comments, top_keywords)
+overall_prevalence <- calculate_keyword_prevalence(filtered_comments, top_keywords)
+
+# Combine the data
+combined_prevalence <- bind_rows(
+  influential_prevalence %>% mutate(group = "Influential Authors"),
+  overall_prevalence %>% mutate(group = "Overall Discussion")
+)
+
+# Create the plot
+keyword_adoption_plot <- ggplot(combined_prevalence, aes(x = Date, y = prevalence, color = group)) +
+  geom_line() +
+  facet_wrap(~word, scales = "free_y", ncol = 4) +
+  labs(title = "Keyword Adoption Over Time: Influential Authors vs Overall Discussion",
+       x = "Date",
+       y = "Keyword Prevalence",
+       color = "Group") +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "bottom")
+
+# Print the plot
+print(keyword_adoption_plot)
+
+# Save the plot
+output_file_path <- file.path(output_directory, "images and tables", "plot_keyword_adoption_over_time.png")
+ggsave(output_file_path, plot = keyword_adoption_plot, width = 16, height = 10, dpi = 300)
+```
+
+```{r Influence Propogation}
+library(igraph)
+library(ggraph)
+library(tidygraph)
+library(dplyr)
+
+# Identify influential authors' threads
+influential_threads <- filtered_comments %>%
+  filter(Author %in% top_influential_authors$Author) %>%
+  select(Thread.ID) %>%
+  distinct()
+
+# Create edges based on who commented after influential authors
+edges <- filtered_comments %>%
+  inner_join(influential_threads, by = "Thread.ID") %>%
+  arrange(Thread.ID, Date) %>%
+  group_by(Thread.ID) %>%
+  mutate(PreviousAuthor = lag(Author)) %>%
+  ungroup() %>%
+  filter(!is.na(PreviousAuthor), 
+         Author != PreviousAuthor,
+         PreviousAuthor %in% top_influential_authors$Author) %>%
+  select(from = PreviousAuthor, to = Author) %>%
+  group_by(from, to) %>%
+  summarise(weight = n(), .groups = "drop") %>%
+  # Filter for stronger connections
+  filter(weight > quantile(weight, 0.25))
+
+# Create graph
+graph <- graph_from_data_frame(edges, directed = TRUE)
+
+# Calculate node sizes based on in-degree
+node_sizes <- degree(graph, mode = "in")
+
+# Identify top 10 influential nodes
+top_nodes <- names(sort(node_sizes, decreasing = TRUE)[1:10])
+
+# Create layout
+layout <- create_layout(graph, layout = "fr")
+
+# Create plot
+influence_plot <- ggraph(layout) + 
+  geom_edge_link(aes(width = weight), alpha = 0.2, arrow = arrow(length = unit(2, 'mm')), end_cap = circle(3, 'mm')) +
+  geom_node_point(aes(size = node_sizes, color = name %in% top_influential_authors$Author)) +
+  geom_node_text(aes(label = ifelse(name %in% top_nodes, name, "")), repel = TRUE, size = 3) +
+  scale_edge_width(range = c(0.1, 2)) +
+  scale_size(range = c(1, 10)) +
+  scale_color_manual(values = c("TRUE" = "red", "FALSE" = "lightblue")) +
+  theme_minimal() +
+  theme(legend.position = "none") +
+  labs(title = "Influence Propagation Network",
+       subtitle = "Node size represents incoming connections, edge width represents frequency of interaction\nRed nodes are influential authors, labeled nodes are top 10 by incoming connections")
+
+# Print the plot
+print(influence_plot)
+
+# Save the plot
+output_file_path <- file.path(output_directory, "images and tables", "plot_influence_propagation_network_improved.png")
+ggsave(output_file_path, plot = influence_plot, width = 20, height = 16, dpi = 300)
+```

### 2024-09-02 Scripts - Data Cleaning and Visuals/New Webpage Visualizations.Rmd
added interactives

--- 2024-09-02 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
@@
 library(SnowballC)
+library(reticulate)
 
@@
 ```
+
 ```{r Get Filtered Comments from Filtered Threads}
@@
 
+```{r Interactive Co-occurrence Network with Plotly, eval=TRUE, include=TRUE}
+# Load necessary library
+library("threejs")
+
+# Prepare data for 3D network
+# We will use the filtered_co_occurrence and term_topic_df from the previous code block
+
+# Create an igraph object from the filtered co-occurrence matrix
+graph_3d <- graph_from_adjacency_matrix(filtered_co_occurrence, weighted = TRUE, mode = "undirected", diag = FALSE)
+
+# Simplify the graph to avoid self-loops and redundant edges
+graph_3d <- simplify(graph_3d)
+
+# Prepare colors based on topic assignment
+topic_colors <- RColorBrewer::brewer.pal(6, "Set1")[term_topic_df$topic]
+
+# Create the 3D force-directed network
+network_3d <- graphjs(
+  graph_3d,
+  vertex.size = log1p(term_frequency[filtered_terms]),
+  vertex.label = V(graph_3d)$name,
+  vertex.color = topic_colors,
+  edge.width = E(graph_3d)$weight / max(E(graph_3d)$weight) * 5,  # Scale edge width
+  main = "Interactive 3D Co-occurrence Network of Key Themes in AIDS Discussion"
+)
+
+# Save the interactive 3D network to an HTML file
+htmlwidgets::saveWidget(network_3d, file = file.path(output_directory, "images and tables/new web visualizations", "interactive_plot_3d_cooccurrence_network.html"))
+```
+
 # Emotional Tone Hypothesis

### 2024-09-02 Scripts - Data Cleaning and Visuals/Old Webpage Visualizations.Rmd
added interactives

--- 2024-09-01 Scripts - Data Cleaning and Visuals/Webpage Visualizations.Rmd
@@
 plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/distribution_of_comments_per_newsgroup.png"))
+plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/old web visualizations/distribution_of_comments_per_newsgroup.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/number_of_threads_over_time.png"))
+plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/number_of_threads_over_time.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/average_comments_per_thread_by_newsgroup.png"))
+plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/average_comments_per_thread_by_newsgroup.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/sentiment_score_distribution_across_all_comments.png"))
+plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/sentiment_score_distribution_across_all_comments.png"))
 plt.show()
@@
 # Save the figure
-plt.savefig(os.path.join(output_directory, "images and tables/top_25_most_active_users_by_newsgroup.png"))
+plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/top_25_most_active_users_by_newsgroup.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/combined_daily_activity_heatmap.png"))
+plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/combined_daily_activity_heatmap.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/word_cloud_all_comments.png"))
+plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/word_cloud_all_comments.png"))
 plt.show()
@@
     # Use f-string to save the file with the specific newsgroup name
-    plt.savefig(os.path.join(output_directory, f"images and tables/word_cloud_{newsgroup}.png"))
+    plt.savefig(os.path.join(output_directory, f"images and tables/old web visualizations/word_cloud_{newsgroup}.png"))
     plt.show()
@@
 plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/growth_of_newsgroups_over_time.png"))
+plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/growth_of_newsgroups_over_time.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/author_engagement_scatterplot.png"))
+plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/author_engagement_scatterplot.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/sentiment_over_time.png"))
+plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/sentiment_over_time.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/sentiment_distribution_by_newsgroup.png"))
+plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/sentiment_distribution_by_newsgroup.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/monthly_sentiment_heatmap.png"))
+plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/monthly_sentiment_heatmap.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/sentiment_over_time_by_newsgroup.png"))
+plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/sentiment_over_time_by_newsgroup.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/sentiment_polarity_distribution.png"))
+plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/sentiment_polarity_distribution.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/sentiment_trend_rolling_average.png"))
+plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/sentiment_trend_rolling_average.png"))
 plt.show()
@@
 plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/word_cloud_positive_sentiment.png"))
+plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/word_cloud_positive_sentiment.png"))
 plt.savefig(0_output_path)
@@
 plt.tight_layout()
-plt.savefig(os.path.join(output_directory, "images and tables/word_cloud_negative_sentiment.png"))
+plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/word_cloud_negative_sentiment.png"))
 plt.show()
@@
 # Save the network graph to an HTML file with full width and height
-network_graph_path <- file.path(output_directory, "images and tables/network_graph.html")
+network_graph_path <- file.path(output_directory, "images and tables/old web visualizations/network_graph.html")
 visSave(network_graph, file = network_graph_path)

### 2024-09-02 Scripts - Data Cleaning and Visuals/New Webpage Visualizations.Rmd
made changes

@@
 
-```{python Python Load Libraries, Directories, and Datasets, eval=FALSE, include=FALSE}
-import os
-import pandas as pd
-import matplotlib.pyplot as plt
-import seaborn as sns
-import numpy as np
-import plotly.express as px
-import plotly.graph_objects as go
-import networkx as nx
-import scipy
-
-# Define directories
-output_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/"
-threads_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads/"
-comments_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments/"
-
-# Load the datasets with the correct file paths
-all_threads = pd.read_csv(os.path.join(threads_directory, "aids_related_threads_82TO86.csv"))
-all_comments = pd.read_csv(os.path.join(comments_directory, "aids_related_comments_82TO86.csv"))
-```
-
 ```{r Filtering For Relevancy}
@@
 # Correctly construct the output file path
-output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_aids_relevancy_filtered.html")
+# output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_aids_relevancy_filtered.html")
 
 # Ensure the directory exists
-dir.create(dirname(output_file_path), recursive = TRUE, showWarnings = FALSE)
+# dir.create(dirname(output_file_path), recursive = TRUE, showWarnings = FALSE)
 
 # Use the constructed path for saving the file
-tab_df(keywords_summary_df, file = output_file_path)
+# tab_df(keywords_summary_df, file = output_file_path)
 ```
@@
 # Save the gt table to an HTML file
-output_file_path <- file.path(output_directory, "images and tables", "table_top_terms_and_betas_(all_authors).html")
-gtsave(gt_table, output_file_path)
+# output_file_path <- file.path(output_directory, "images and tables", "table_top_terms_and_betas_(all_authors).html")
+# gtsave(gt_table, output_file_path)
 ```
@@
 co_occurrence <- crossprod(as.matrix(dtm)) # Create co-occurrence matrix
+
+binary_dtm <- as.matrix(dtm)
+binary_dtm[binary_dtm > 0] <- 1  # Convert counts to 1s
+
+# Step 2: Calculate document frequency for each term
+term_frequency <- colSums(binary_dtm)
+
 # Set a threshold to filter less relevant terms based on frequency
-term_frequency <- rowSums(co_occurrence) # Calculate term frequency
 threshold <- quantile(term_frequency, 0.75) # Set threshold for top 25% most frequent terms
@@
 # Save the plot to a PNG file with increased size
-ggsave(file.path(output_directory, "images and tables", "plot_co-occurrence_network.png"), 
-       plot = co_occurrence_plot, width = 20, height = 16, dpi = 300)  # Increased dimensions
-```
-
-```{r Interactive Co-occurrence Network with Plotly, eval=TRUE, include=TRUE}
-# Load necessary library
-library("threejs")
-
-# Prepare data for 3D network
-# We will use the filtered_co_occurrence and term_topic_df from the previous code block
-
-# Create an igraph object from the filtered co-occurrence matrix
-graph_3d <- graph_from_adjacency_matrix(filtered_co_occurrence, weighted = TRUE, mode = "undirected", diag = FALSE)
-
-# Simplify the graph to avoid self-loops and redundant edges
-graph_3d <- simplify(graph_3d)
-
-# Prepare colors based on topic assignment
-topic_colors <- RColorBrewer::brewer.pal(6, "Set1")[term_topic_df$topic]
-
-# Create the 3D force-directed network
-network_3d <- graphjs(
-  graph_3d,
-  vertex.size = log1p(term_frequency[filtered_terms]),
-  vertex.label = V(graph_3d)$name,
-  vertex.color = topic_colors,
-  edge.width = E(graph_3d)$weight / max(E(graph_3d)$weight) * 5,  # Scale edge width
-  main = "Interactive 3D Co-occurrence Network of Key Themes in AIDS Discussion"
-)
-
-# Save the interactive 3D network to an HTML file
-htmlwidgets::saveWidget(network_3d, file = file.path(output_directory, "images and tables/new web visualizations", "interactive_plot_3d_cooccurrence_network.html"))
+# ggsave(file.path(output_directory, "images and tables", "plot_co-occurrence_network.png"), 
+#       plot = co_occurrence_plot, width = 20, height = 16, dpi = 300)  # Increased dimensions
 ```
@@
 
-output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_influential_authors.html")
-tab_df(influential_authors_metadata_with_totals, file = output_file_path)
+# output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_influential_authors.html")
+# tab_df(influential_authors_metadata_with_totals, file = output_file_path)
 ```
@@
 # Correctly construct the output file path
-output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_sentiment_scores_combined.html")
+# output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_sentiment_scores_combined.html")
 
@@
 # Display the combined descriptive statistics table using sjPlot
-tab_df(
-  combined_sentiment_stats,
-  title = "Descriptive Statistics for Sentiment Scores of Different Datasets",
-  show.rownames = FALSE,
-  show.ci = FALSE,
-  show.p = FALSE,
-  digits = 2,
-  file = output_file_path)
+# tab_df(
+  #combined_sentiment_stats,
+  #title = "Descriptive Statistics for Sentiment Scores of Different Datasets",
+  #show.rownames = FALSE,
+  #show.ci = FALSE,
+  #show.p = FALSE,
+  #digits = 2,
+  #file = output_file_path)
 ```
@@
 # Save the plot to a PNG file
-output_file_path <- file.path(output_directory, "images and tables", "plot_time_series_sentiment_line_graph.png")
-ggsave(output_file_path, plot = time_series_plot, width = 10, height = 6, dpi = 300)
+# output_file_path <- file.path(output_directory, "images and tables", "plot_time_series_sentiment_line_graph.png")
+# ggsave(output_file_path, plot = time_series_plot, width = 10, height = 6, dpi = 300)
 ```
@@
 # Save the gt table to an HTML file
-output_file_path <- file.path(output_directory, "images and tables", "table_top_terms_and_betas_(influential_authors).html")
-gtsave(gt_table, output_file_path)
+# output_file_path <- file.path(output_directory, "images and tables", "table_top_terms_and_betas_(influential_authors).html")
+# gtsave(gt_table, output_file_path)
 ```
@@
 
-output_file_path <- file.path(output_directory, "images and tables", "table_topic_matches.html")
-
-tab_df(best_matches, ,
-  file = output_file_path)
+#output_file_path <- file.path(output_directory, "images and tables", "table_topic_matches.html")
+
+#tab_df(best_matches, ,
+ #file = output_file_path)
 
@@
 
-output_file_path_transposed <- file.path(output_directory, "images and tables", "table_topic_matches_transposed.html")
-tab_df(transposed_best_matches,
-  file = output_file_path_transposed)
+# output_file_path_transposed <- file.path(output_directory, "images and tables", "table_topic_matches_transposed.html")
+# tab_df(transposed_best_matches, file = output_file_path_transposed)
 ```
@@
 
-ggsave(file.path(output_directory, "images and tables", "plot_topic_influence_comparison_bar_graph.png"), 
-       width = 10, height = 6, dpi = 300)
+# ggsave(file.path(output_directory, "images and tables", "plot_topic_influence_comparison_bar_graph.png"), width = 10, height = 6, dpi = 300)
 ```
@@
 # Save the plot with a higher DPI for better clarity
-output_file_path <- file.path(output_directory, "images and tables", "plot_topic_prevalence_line_graph.png")
-ggsave(output_file_path, plot = line_plot, width = 12, height = 8, dpi = 300)
+# output_file_path <- file.path(output_directory, "images and tables", "plot_topic_prevalence_line_graph.png")
+# ggsave(output_file_path, plot = line_plot, width = 12, height = 8, dpi = 300)
 ```
@@
 # Save the plot to a file
-output_file_path <- file.path(output_directory, "images and tables/plot_top_15_most_active_users_by_newsgroup.png")
-ggsave(output_file_path, plot = bar_plot, width = 10, height = 6, dpi = 300)
-```
+# output_file_path <- file.path(output_directory, "images and tables/plot_top_15_most_active_users_by_newsgroup.png")
+# ggsave(output_file_path, plot = bar_plot, width = 10, height = 6, dpi = 300)
+```
+
 ```{r Thematic evolution}
@@
 # Save the plot
-output_file_path <- file.path(output_directory, "images and tables", "plot_keyword_adoption_over_time.png")
-ggsave(output_file_path, plot = keyword_adoption_plot, width = 16, height = 10, dpi = 300)
+# output_file_path <- file.path(output_directory, "images and tables", "plot_keyword_adoption_over_time.png")
+# ggsave(output_file_path, plot = keyword_adoption_plot, width = 16, height = 10, dpi = 300)
 ```
@@
 # Save the plot
-output_file_path <- file.path(output_directory, "images and tables", "plot_influence_propagation_network_improved.png")
-ggsave(output_file_path, plot = influence_plot, width = 20, height = 16, dpi = 300)
-```
+# output_file_path <- file.path(output_directory, "images and tables", "plot_influence_propagation_network_improved.png")
+# ggsave(output_file_path, plot = influence_plot, width = 20, height = 16, dpi = 300)
+```

### 2024-09-02 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
made changes

@@
   scale_fill_brewer(palette = "Set1", guide = "none") +  # Remove fill from legend
-  coord_cartesian(xlim = c(-8, 8), ylim = c(-8, 8)) +
+  coord_cartesian(xlim = c(-9, 9), ylim = c(-9, 9)) +
   theme_void(base_size = 16) +
@@
 ```
+# For Webpage
+
+```{r Interactive Co-Occurance Network of Top Terms, eval=TRUE}
+# Load necessary libraries
+library(visNetwork)
+library(igraph)
+
+library(visNetwork)
+library(igraph)
+
+# Create an igraph object from the filtered co-occurrence matrix
+graph_3d <- graph_from_adjacency_matrix(filtered_co_occurrence, weighted = TRUE, mode = "undirected", diag = FALSE)
+
+# Simplify the graph to avoid self-loops and redundant edges
+graph_3d <- simplify(graph_3d)
+
+# Prepare colors based on topic assignment
+topic_colors <- RColorBrewer::brewer.pal(6, "Set1")[term_topic_df$topic]
+
+# Prepare data for visNetwork
+nodes <- data.frame(
+  id = V(graph_3d)$name,
+  label = V(graph_3d)$name,  # Labels are always visible
+  group = term_topic_df$topic,  # Group nodes by topic
+  value = log1p(term_frequency[filtered_terms]) * 8,  # Increase node size scaling for visibility
+  title = paste("<p><b>Node:</b>", V(graph_3d)$name, "<br><b>Frequency:</b>", term_frequency[filtered_terms], "</p>")  # Custom hover popups
+)
+
+# Sort nodes alphabetically by label
+nodes <- nodes[order(nodes$label), ]
+
+edges <- data.frame(
+  from = as.character(ends(graph_3d, E(graph_3d))[, 1]),
+  to = as.character(ends(graph_3d, E(graph_3d))[, 2]),
+  value = E(graph_3d)$weight / max(E(graph_3d)$weight) * 1,  # Scale edge width for visibility
+  label = round(E(graph_3d)$weight, 2)  # Add edge labels
+)
+
+network_vis <- visNetwork(nodes, edges, width = "100%", height = "90vh") %>%
+  visNodes(
+    shape = "dot",
+    scaling = list(min = 5, max = 30),
+    font = list(size = 35),
+    color = list(
+      background = topic_colors,
+      border = "black",
+      highlight = "red"
+    ),
+    title = nodes$title
+  ) %>%
+  visEdges(
+    width = ~value,
+    color = list(color = 'gray', highlight = 'red'),
+    smooth = list(enabled = TRUE, type = "continuous", roundness = 1)
+  ) %>%
+  visOptions(
+    highlightNearest = list(enabled = TRUE, hover = TRUE),
+    nodesIdSelection = list(enabled = TRUE, useLabels = TRUE, main = "Select by term"),  # Changed label for node selection
+    selectedBy = list(variable = "group", sort = TRUE, main = "Select by topic")  # Changed label for group selection
+  ) %>%
+  visPhysics(
+    stabilization = FALSE,
+    solver = "barnesHut",
+    barnesHut = list(
+      gravitationalConstant = -30000,  # Increase negative value for stronger repulsion
+      springLength = 500,              # Increase spring length to spread nodes apart
+      springConstant = 0.01            # Decrease spring constant for more flexible edges
+    )
+  ) %>%
+  visInteraction(
+    dragNodes = TRUE,
+    dragView = TRUE,
+    zoomView = TRUE,
+    navigationButtons = TRUE,  # Adds navigation buttons
+    keyboard = TRUE
+  ) %>%
+  visLayout(
+    improvedLayout = TRUE
+  )
+
+# Save the network graph to an HTML file with full width and height
+network_graph_path <- file.path(output_directory, "images and tables/new web visualizations/interactive_plot_3d_cooccurrence_network.html")
+visSave(network_vis, file = network_graph_path)
+
+# Custom title and legend creation in HTML
+title_html <- '
+<div style="position: absolute; top: 40px; left: 50%; transform: translateX(-50%); font-size: 24px; font-weight: bold; font-family: Arial, sans-serif;">
+  Interactive Co-Occurrence Network of Top Terms
+</div>
+'
+
+legend_html <-'
+<div style="position: absolute; top: 40px; right: 40px; background-color: #f0f0f0; border: 1px solid #666; padding: 7px; text-padding: 7px; border-radius: 5px; font-family: Arial, sans-serif;">
+  <span style="color: #94df5c;">●</span> Topic 1
+  <span style="color: #ffff54;">●</span> Topic 2
+  <span style="color: #eb8584;">●</span> Topic 3<br>
+  <span style="color: #a787de;">●</span> Topic 4
+  <span style="color: #dd82ee;">●</span> Topic 5
+  <span style="color: #9fc0f7;">●</span> Topic 6
+</div>
+'
+
+# Inject the custom title and legend into the HTML file
+html_content <- readLines(network_graph_path)
+html_content <- c(title_html, html_content, legend_html)
+writeLines(html_content, network_graph_path)
+```
